\settowidth{\versewidth}{let the sea and all within it thunder praise,}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{011 11 11 11 11 11 11 101 101 101}
\FirstLetter{O} sing a new song to the L\pointup{o}rd,\Flex\\
sing to the Lord \pointup{a}ll the earth.\Med\\
O sing to the Lord, bless h\pointup{\i}s name.

Proclaim his help day by d\pointup{a}y,\Flex\\
tell among the nat\pointup{\i}ons his glory\Med\\
and his wonders among all th\pointup{e} peoples.

The Lord is great and worthy of pr\pointup{a}ise,\Flex\\
to be feared ab\pointup{o}ve all gods;\Med\\
the gods of the heathens \pointup{a}re naught.

It was the Lord who made the heav\pointup{e}ns,\Flex\\
his are majesty and st\pointup{a}te and power\Med\\
and splendor in his hol\pointup{y} place.

Give the Lord, you families of peopl\pointup{e}s,\Flex\\
give the Lord glor\pointup{y} and power;\Med\\
give the Lord the glory of h\pointup{\i}s name.

Bring an offering and enter his c\pointup{o}urts,\Flex\\
worship the Lord \pointup{\i}n his temple.\Med\\
O earth, tremble b\pointup{e}fore him.

Proclaim to the nations: God is k\pointup{\i}ng.\Flex\\
The world he made firm \pointup{\i}n its place;\Med\\
he will judge the people \pointup{\i}n fairness.

Let the heavens rejoice and \pointup{e}arth be glad,\Med\\
let the sea and all within it thund\pointup{e}r praise,\\
let the land and all it b\pointup{e}ars rejoice,\Med\\
all the trees of the wood shout f\pointup{o}r joy

at the presence of the Lord f\pointup{o}r he comes,\Med\\
he comes to rule th\pointup{e} earth.\\
With justice he will r\pointup{u}le the world,\Med\\
he will judge the peoples with h\pointup{\i}s truth.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
