\settowidth{\versewidth}{Behold, the nations count as a drop of the bucket, +}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 1011 1011 11 101 101}
\FirstLetter{H}ere comes with power th\pointup{e} Lord God,\Med\\
who rules by his str\pointup{o}ng arm;\\
here is his reward w\pointup{\i}th him,\Med\\
his recompense b\pointup{e}fore him.

Like a shepherd he feeds h\pointup{\i}s flock;\Med\\
in his arms he gathers th\pointup{e} lambs,\\
Carrying them in h\pointup{\i}s bosom,\Med\\
and leading the ewes w\pointup{\i}th care.

Who has cupped in his hand the waters of th\pointup{e} sea,\Med\\
and marked off the heavens with \pointup{a} span?\\
Who has held in a measure the dust of the \pointup{e}arth,\Flex\\
weighed the mountains \pointup{\i}n scales\Med\\
and the hills in \pointup{a} balance?

Who has directed the spirit of th\pointup{e} Lord,\Med\\
or has instructed him as h\pointup{\i}s counselor?\\
Whom did he consult to gain knowl\pointup{e}dge?\Flex\\
Who taught him the path \pointup{o}f judgment,\Med\\
or showed him the way of und\pointup{e}rstanding?

Behold, the nations count as a drop of the buck\pointup{e}t,\Flex\\
as dust on th\pointup{e} scales;\Med\\
the coastlands weigh no more th\pointup{a}n powder.

Lebanon would not suffice f\pointup{o}r fuel,\Med\\
nor its animals be enough for hol\pointup{o}causts.\\
Before him all the nations are \pointup{a}s nought,\Med\\
as nothing and void he \pointup{a}ccounts them.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{psalmverse}
