\settowidth{\versewidth}{though the mountains fall into the depths of the sea;}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{010101 1 10101 1 101011 1 101}
\FirstLetter{G}od is for us a ref\pointup{u}ge and strength,\Med\\
a helper close at hand, in time of d\pointup{i}stress,\\
so we shall not fear though the \pointup{e}arth should rock,\Med\\
though the mountains fall into the depths of th\pointup{e} sea;\\
even though its waters r\pointup{a}ge and foam,\Med\\
even though the mountains be shaken by \pointup{i}ts waves.

The Lord of hosts \pointup{i}s with us:\Med\\
the God of Jacob is \pointup{o}ur stronghold.

The waters of a river give joy t\pointup{o} God’s city,\Med\\
the holy place where the Most H\pointup{i}gh dwells.\\
God is within, it cann\pointup{o}t be shaken;\Med\\
God will help it at the dawning of th\pointup{e} day.\\
Nations are in tumult, kingd\pointup{o}ms are shaken:\Med\\
he lifts his voice, the earth shrinks \pointup{a}way.

The Lord of hosts \pointup{i}s with us:\Med\\
the God of Jacob is \pointup{o}ur stronghold.

Come, consider the works \pointup{o}f the Lord,\Med\\
the redoubtable deeds he has done on th\pointup{e} earth.\\
He puts an end to wars over \pointup{a}ll the earth;\Med\\
the bow he breaks, the spear h\pointup{e} snaps.\\
He burns the shields with f\pointup{i}re.\Flex\\
“Be still and know that \pointup{I} am God,\Med\\
supreme among the nations, supreme on th\pointup{e} earth!”

The Lord of hosts \pointup{i}s with us:\Med\\
the God of Jacob is \pointup{o}ur stronghold.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{i}ng, is now,\Med\\
and will be forever. \pointup{A}men. 
  \end{patverse}
\end{psalmverse}
