\settowidth{\versewidth}{that will come upon the people who attack us.}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01011 101 1101 101 101 101 101 11 101}
\FirstLetter{O} Lord, I have heard y\pointup{o}ur renown,\Med\\
and feared, O Lord, y\pointup{o}ur work.\\
In the course of the years revive \pointup{\i}t,\Flex\\
in the course of the years m\pointup{a}ke it known;\Med\\
in your wrath remember c\pointup{o}mpassion!

God c\pointup{o}mes from Teman,\Med\\
the Holy One from M\pointup{o}unt Paran.\\
Covered are the heavens w\pointup{\i}th his glory,\Med\\
and with his praise the earth \pointup{\i}s filled.

His splendor spreads like the l\pointup{\i}ght;\Flex\\
rays shine forth fr\pointup{o}m beside him,\Med\\
where his power is c\pointup{o}ncealed.\\
You come forth to s\pointup{a}ve your people,\Med\\
to save your \pointup{a}nointed one.

You tread the sea w\pointup{\i}th your steeds\Med\\
amid the churning of the d\pointup{e}ep waters.\\
I hear, and my b\pointup{o}dy trembles;\Med\\
at the sound, my l\pointup{\i}ps quiver.

Decay inv\pointup{a}des my bones,\Med\\
my legs tremble b\pointup{e}neath me.\\
I await the day \pointup{o}f distress\Med\\
that will come upon the people who \pointup{a}ttack us.

For though the fig tree bl\pointup{o}ssom not\Med\\
nor fruit be on th\pointup{e} vines,\\
though the yield of the \pointup{o}live fail\Med\\
and the terraces produce n\pointup{o} nourishment,

though the flocks disappear fr\pointup{o}m the fold\Med\\
and there be no herd in th\pointup{e} stalls,\\
yet will I rejoice \pointup{\i}n the Lord\Med\\
and exult in my sav\pointup{\i}ng God.

God, my Lord, is my str\pointup{e}ngth;\Flex\\
he makes my feet swift as th\pointup{o}se of hinds\Med\\
and enables me to go upon th\pointup{e} heights.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
