\settowidth{\versewidth}{like the grass which springs up in the morning.}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{01011 1011 101 101 101 101 101 101 1011 101}
\FirstLetter{O} Lord, you have b\pointup{e}en our refuge\Med\\
from one generation to th\pointup{e} next.\\
Before the mountains were b\pointup{o}rn\Flex\\
or the earth or the w\pointup{o}rld brought forth,\Med\\
you are God, without beginning \pointup{o}r end.

You turn men b\pointup{a}ck to dust\Med\\
and say: Go back, sons \pointup{o}f men.\\
To your eyes a thousand y\pointup{e}ars\Flex\\
are like yesterday, c\pointup{o}me and gone,\Med\\
no more than a watch in th\pointup{e} night.

You sweep men away l\pointup{\i}ke a dream,\Med\\
like the grass which springs up in th\pointup{e} morning.\\
In the morning it springs \pointup{u}p and flowers:\Med\\
by evening it withers \pointup{a}nd fades.

So we are destroyed \pointup{\i}n your anger,\Med\\
struck with terror in y\pointup{o}ur fury.\\
Our guilt lies op\pointup{e}n before you;\Med\\
our secrets in the light of y\pointup{o}ur face.

All our days pass away \pointup{\i}n your anger.\Med\\
Our life is over like \pointup{a} sigh.\\
Our span is sev\pointup{e}nty years,\Med\\
or eighty for those who \pointup{a}re strong.

And most of these are emptin\pointup{e}ss and pain.\Med\\
They pass swiftly and we \pointup{a}re gone.\\
Who understands the power \pointup{o}f your anger\Med\\
and fears the strength of y\pointup{o}ur fury?

Make us know the shortness \pointup{o}f our life\Med\\
that we may gain wisdom \pointup{o}f heart.\\
Lord, relent! Is your ang\pointup{e}r for ever?\Med\\
Show pity to y\pointup{o}ur servants.

In the morning, fill us w\pointup{\i}th your love;\Med\\
we shall exult and rejoice all \pointup{o}ur days.\\
Give us joy to balance \pointup{o}ur affliction\Med\\
for the years when we knew m\pointup{\i}sfortune.

Show forth your work t\pointup{o} your servants;\Med\\
let your glory shine on th\pointup{e}ir children.\\
Let the favor of the Lord be upon \pointup{u}s:\Flex\\
give success to the work \pointup{o}f our hands,\Med\\
give success to the work of \pointup{o}ur hands.

Glory to the Father, and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit;\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be for ever, \pointupl{A}men.
  \end{patverse}
\end{verse}
