\settowidth{\versewidth}{Yet basely has he been treated by his degenerate children, *}
\begin{verse}%%[\versewidth]%
  \begin{patverse}
    \indentpattern{010101 10101 10101 101 10101 101 10101 101}
\FirstLetter{G}ive ear, O heavens, wh\pointup{\i}le I speak;\Med\\
let the earth hearken to the words of m\pointup{y} mouth!\\
May my instruction soak in l\pointup{\i}ke the rain,\Med\\
and my discourse permeate like th\pointup{e} dew,\\
Like a downpour up\pointup{o}n the grass,\Med\\
like a shower upon th\pointup{e} crops.

For I will sing the L\pointup{o}rd’s renown.\Med\\
Oh, proclaim the greatness of \pointup{o}ur God!\\
The Rock---how faultless \pointup{a}re his deeds,\Med\\
how right all h\pointup{\i}s ways!\\
A faithful God, with\pointup{o}ut deceit,\Med\\
how just and upright h\pointup{e} is!

Yet basely has he been treated by his degen\pointup{e}rate children,\Med\\
a perverse and crook\pointup{e}d race!\\
Is the Lord to be thus rep\pointup{a}id by you,\Med\\
O stupid and fool\pointup{\i}sh people?\\
Is he not your father wh\pointup{o} created you?\Med\\
Has he not made you and \pointup{e}stablished you?

Think back on the d\pointup{a}ys of old,\Med\\
reflect on the years of age up\pointup{o}n age.\\
Ask your father and he w\pointup{\i}ll inform you,\Med\\
ask your elders and they w\pointup{\i}ll tell you:

When the Most High assigned the nat\pointup{\i}ons their heritage,\Med\\
when he parceled out the descendants \pointup{o}f Adam,\\
he set up the boundaries \pointup{o}f the peoples\Med\\
after the number of the sons \pointup{o}f God;\\
while the Lord’s own port\pointup{\i}on was Jacob,\Med\\
his hereditary share w\pointup{a}s Israel.

He found them \pointup{\i}n a wilderness,\Med\\
a wasteland of howl\pointup{\i}ng desert.\\
He shielded them and c\pointup{a}red for them,\Med\\
guarding them as the apple of h\pointup{\i}s eye.

As an eagle incites its n\pointup{e}stlings forth\Med\\
by hovering over \pointup{\i}ts brood,\\
so he spread his wings t\pointup{o} receive them\Med\\
and bore them up on h\pointup{\i}s pinions.\\
The Lord alone w\pointup{a}s their leader,\Med\\
no strange god was w\pointup{\i}th him.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be for ever. \pointupl{A}men.
  \end{patverse}
\end{verse}
