\begin{verse}
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 01 101 01 101 1001 101 }
Turn your ear, O Lord, and g\pointup{\i}ve answer\Med\\
for I am poor \pointup{a}nd needy.\\
Preserve my life, for I \pointup{a}m faithful;\Med\\
save the servant who trusts \pointup{i}n you.

You are my God, have mercy on m\pointup{e}, Lord,\Med\\
for I cry to you all the d\pointup{a}y long.\\
Give joy to your servant, \pointup{O} Lord,\Med\\
for to you I lift up m\pointup{y} soul.

O Lord, you are good and f\pointup{o}rgiving,\Med\\
full of love to all wh\pointup{o} call.\\
Give heed, O Lord, to m\pointup{y} prayer\Med\\
and attend to the sound of m\pointup{y} voice.

In the day of distress I w\pointup{\i}ll call\Med\\
and surely you will r\pointup{e}ply.\\
Among the gods there is none like you, \pointup{O} Lord;\Med\\
nor work to compare w\pointup{\i}th yours.

All the nations shall come to \pointup{a}dore you\Med\\
and glorify your name, \pointup{O} Lord:\\
for you are great and do marvel\pointup{o}us deeds,\Med\\
you who alone \pointup{a}re God.

Show me, Lord, your w\pointup{a}y\Flex\\
so that I may walk in y\pointup{o}ur truth.\Med\\
Guide my heart to fear y\pointup{o}ur name.

I will praise you, Lord my God, with all m\pointup{y} heart\Med\\
and glorify your name f\pointup{o}r ever;\\
for your love to me has b\pointup{e}en great:\Med\\
you have saved me from the depths of th\pointup{e} grave.

The proud have risen against m\pointup{e};\Flex\\
ruthless men seek m\pointup{y} life;\Med\\
to you they pay n\pointup{o} heed.

But you, God of mercy and comp\pointup{a}ssion,\Med\\
slow to anger, \pointup{O} Lord,\\
abounding in love \pointup{a}nd truth,\Med\\
turn and take pity \pointup{o}n me.

O give your strength to y\pointup{o}ur servant\Med\\
and save your handm\pointup{a}id’s son.\\
Show me the sign of your fav\pointup{o}r\Flex\\
that my foes may see to th\pointup{e}ir shame\Med\\
that you console me and give me y\pointup{o}ur help.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{i}s now,\Med\\
and will be forever. \pointup{A}men.
  \end{patverse}
\end{verse}
