\settowidth{\versewidth}{Let us bless the Father, and the Son, and the Holy Spirit. *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01010101 101010101 101010101 1010101 101}
    \FirstLetter{B}less the Lord, all you works \pointup{o}f the Lord.\Med\\
Praise and exalt him above \pointup{a}ll forever.\\
Angels of the Lord, bl\pointup{e}ss the Lord.\Med\\
You heavens, bl\pointup{e}ss the Lord.\\
All you waters above the heavens, bl\pointup{e}ss the Lord.\Med\\
All you hosts of the Lord, bl\pointup{e}ss the Lord.\\
Sun and moon, bl\pointup{e}ss the Lord.\Med\\
Stars of heaven, bl\pointup{e}ss the Lord.

Every shower and dew, bl\pointup{e}ss the Lord.\Med\\
All you winds, bl\pointup{e}ss the Lord.\\
Fire and heat, bl\pointup{e}ss the Lord.\Med\\
Cold and chill, bl\pointup{e}ss the Lord.\\
Dew and rain, bl\pointup{e}ss the Lord.\Med\\
Frost and chill, bl\pointup{e}ss the Lord.\\
Ice and snow, bl\pointup{e}ss the Lord.\Med\\
Nights and days, bl\pointup{e}ss the Lord.\\
Light and darkness, bl\pointup{e}ss the Lord.\Med\\
Lightnings and clouds, bl\pointup{e}ss the Lord.

Let the earth bl\pointup{e}ss the Lord.\Med\\
Praise and exalt him above \pointup{a}ll forever.\\
Mountains and hills, bl\pointup{e}ss the Lord.\Med\\
Everything growing from the earth, bl\pointup{e}ss the Lord.\\
You springs, bl\pointup{e}ss the Lord.\Med\\
Seas and rivers, bl\pointup{e}ss the Lord.\\
You dolphins and all water creatures, bl\pointup{e}ss the Lord.\Med\\
All you birds of the air, bl\pointup{e}ss the Lord.\\
All you beasts, wild and tame, bl\pointup{e}ss the Lord.\Med\\
You sons of men, bl\pointup{e}ss the Lord.

O Israel, bl\pointup{e}ss the Lord.\Med\\
Praise and exalt him above \pointup{a}ll forever.\\
Priests of the Lord, bl\pointup{e}ss the Lord.\Med\\
Servants of the Lord, bl\pointup{e}ss the Lord.\\
Spirits and souls of the just, bl\pointup{e}ss the Lord.\Med\\
Holy men of humble heart, bl\pointup{e}ss the Lord.\\
Hananiah, Azariah, Mishael, bl\pointup{e}ss the Lord.\Med\\
Praise and exalt him above \pointup{a}ll forever.

Let us bless the Father, and the Son, and the H\pointup{o}ly Spirit.\Med\\
Let us praise and exalt him above \pointup{a}ll forever.\\
Blessed are you, Lord, in the firmam\pointup{e}nt of heaven.\Med\\
Praiseworthy and glorious and exalted above \pointup{a}ll forever.
  \end{patverse}
\end{verse}
