\settowidth{\versewidth}{you surround him with favour as with a shield.}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 11 101 101 1 101}
    \FirstLetter{T}o my words give ear, \pointup{O} Lord,\Med\\
    give heed to m\pointup{y} groaning.\\
    Attend to the sound of m\pointup{y} cries,\Med\\
    my King and m\pointup{y} God.

It is you whom I invoke, \pointup{O} Lord.\Med\\
    In the morning y\pointup{o}u hear me;\\
in the morning I offer you m\pointup{y} prayer,\Med\\
    watching \pointup{a}nd waiting.

You are no God who l\pointup{o}ves evil;\Med\\
    no sinner is y\pointup{o}ur guest.\\
The boastful shall not stand th\pointup{e}ir ground\Med\\
    before y\pointup{o}ur face.

You hate all who d\pointup{o} evil;\Med\\
    you destroy all wh\pointup{o} lie.\\
The deceitful and bloodthirst\pointup{y} man\Med\\
    the Lord d\pointup{e}tests.

But I through the greatness of y\pointup{o}ur love\Med\\
    have access to y\pointup{o}ur house.\\
I bow down before your hol\pointup{y} temple,\Med\\
    filled w\pointup{\i}th awe.

Lead me, Lord, in your just\pointup{\i}ce,\Flex\\
    because of those who lie \pointup{\i}n wait;\Med\\
    make clear your way b\pointup{e}fore me.

No truth can be found in th\pointup{e}ir mouths,\Med\\
    their heart is \pointup{a}ll mischief,\\
their throat a wide-op\pointup{e}n grave,\Med\\
    all honey th\pointup{e}ir speech.

All those you protect shall b\pointup{e} glad\Med\\
    and ring out th\pointup{e}ir joy.\\
You shelter them; in you they r\pointup{e}joice,\Med\\
    those who love y\pointup{o}ur name.

It is you who bless the just m\pointup{a}n, Lord:\Med\\
    you surround him with favour as with \pointup{a} shield.

Glory to the Father and to th\pointup{e} Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
    and will be for ever. \pointupl{A}men.
  \end{patverse}
\end{psalmverse}
