\settowidth{\versewidth}{“Turn back, you sinners! do the right before him: +}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01 101 11 11 101 101 101 1011 101 101}
    \FirstLetter{B}lessed be God who lives f\pointup{o}rever,\Med\\
    because his kingdom lasts for \pointup{a}ll ages.

    For he scourges and then h\pointup{a}s mercy;\Med\\
    he casts down to the depths of the neth\pointup{e}r world,\\
    and he brings up from the great \pointup{a}byss.\Med\\
    No one can escape h\pointup{\i}s hand.

    Praise him, you Israelites, before the Gent\pointup{\i}les,\Flex\\
    for though he has scattered you \pointup{a}mong them,\Med\\
    he has shown you his greatness ev\pointup{e}n there.

    Exalt him before every living be\pointup{\i}ng,\Flex\\
    because he is the Lord \pointup{o}ur God,\Med\\
    our Father and God f\pointup{o}rever.

    He scourged you for your \pointup{\i}niquities,\Med\\
    but will again have mercy on y\pointup{o}u all.\\
    He will gather you from all th\pointup{e} Gentiles\Med\\
    among whom you have b\pointup{e}en scattered.

    When you turn back to him with all y\pointup{o}ur heart,\Med\\
    to do what is right b\pointup{e}fore him,\\
    Then he will turn back t\pointup{o} you,\Med\\
    and no longer hide his face fr\pointup{o}m you.

    So now consider what he has done f\pointup{o}r you,\Med\\
    and praise him with f\pointup{u}ll voice.\\
    Bless the Lord \pointup{o}f righteousness,\Med\\
    and exalt the King of th\pointup{e} ages.

    In the land of my exile \pointup{I} praise him,\Med\\
    and show his power and majesty to a sinf\pointup{u}l nation.\\
    “Turn back, you sinners! do the right before h\pointup{\i}m:\Flex\\
    perhaps he may look with favor \pointup{u}pon you\Med\\
    and show y\pointup{o}u mercy.

    “As for me, I exalt m\pointup{y} God,\Med\\
    and my spirit rejoices in the King \pointup{o}f heaven.\\
    Let all people speak of h\pointup{\i}s majesty,\Med\\
    and sing his praises in J\pointup{e}rusalem.”

    Glory to the Father and to th\pointup{e} Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
    as it was in the beginning, \pointup{\i}s now,\Med\\
    and will be for ever. \pointupl{A}men.
  \end{patverse}
\end{verse}
