\settowidth{\versewidth}{I will hear what the Lord God has to say, *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{010101 101 101 10101 101 101 101}
\FirstLetter{O} Lord, you once fav\pointup{o}red your land\Med\\
and revived the fortunes \pointup{o}f Jacob,\\
you forgave the guilt \pointup{o}f your people\Med\\
and covered all th\pointup{e}ir sins.\\
You averted \pointup{a}ll your rage,\Med\\
you calmed the heat of y\pointup{o}ur anger.

Revive us now, G\pointup{o}d, our helper!\Med\\
Put an end to your grievance \pointup{a}gainst us.\\
Will you be angry with \pointup{u}s for ever,\Med\\
will your anger nev\pointup{e}r cease?

Will you not restore ag\pointup{a}in our life\Med\\
that your people may rejoice \pointup{\i}n you?\\
Let us see, O L\pointup{o}rd, your mercy\Med\\
and give us your sav\pointup{\i}ng help.

I will hear what the Lord God h\pointup{a}s to say,\Med\\
a voice that speaks \pointup{o}f peace,\\
peace for his people \pointup{a}nd his friends\Med\\
and those who turn to him in th\pointup{e}ir hearts.\\
His help is near for th\pointup{o}se who fear him\Med\\
and his glory will dwell in \pointup{o}ur land.

Mercy and faithfuln\pointup{e}ss have met;\Med\\
justice and peace have \pointup{e}mbraced.\\
Faithfulness shall spring fr\pointup{o}m the earth\Med\\
and justice look down fr\pointup{o}m heaven.

The Lord will m\pointup{a}ke us prosper\Med\\
and our earth shall yield \pointup{\i}ts fruit.\\
Justice shall m\pointup{a}rch before him\Med\\
and peace shall follow h\pointup{\i}s steps.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
