\begin{verse}
  \begin{patverse}
    \indentpattern{01011 101 1101 101 101 101 101 11 101}
\FirstLetter{O} Lord, I have heard your r\pointup{e}nown,\Med\\
and feared, O Lord, y\pointup{o}ur work.\\
In the course of the years revive \pointup{\i}t,\Flex\\
in the course of the years make \pointup{\i}t known;\Med\\
in your wrath remember c\pointup{o}mpassion!

God comes fr\pointup{o}m Teman,\Med\\
the Holy One from M\pointup{o}unt Paran.\\
Covered are the heavens with h\pointup{\i}s glory,\Med\\
and with his praise the earth \pointup{\i}s filled.

His splendor spreads like the l\pointup{\i}ght;\Flex\\
rays shine forth from b\pointup{e}side him,\Med\\
where his power is c\pointup{o}ncealed.\\
You come forth to save y\pointup{o}ur people,\Med\\
to save your \pointup{a}nointed one.

You tread the sea with y\pointup{o}ur steeds\Med\\
amid the churning of the d\pointup{e}ep waters.\\
I hear, and my bod\pointup{y} trembles;\Med\\
at the sound, my l\pointup{\i}ps quiver.

Decay invades m\pointup{y} bones,\Med\\
my legs tremble b\pointup{e}neath me.\\
I await the day of d\pointup{\i}stress\Med\\
that will come upon the people who \pointup{a}ttack us.

For though the fig tree bloss\pointup{o}m not\Med\\
nor fruit be on th\pointup{e} vines,\\
though the yield of the ol\pointup{\i}ve fail\Med\\
and the terraces produce n\pointup{o} nourishment,

though the flocks disappear from th\pointup{e} fold\Med\\
and there be no herd in th\pointup{e} stalls,\\
yet will I rejoice in th\pointup{e} Lord\Med\\
and exult in my sav\pointup{\i}ng God.

God, my Lord, is my str\pointup{e}ngth;\Flex\\
he makes my feet swift as those \pointup{o}f hinds\Med\\
and enables me to go upon th\pointup{e} heights.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
