\settowidth{\versewidth}{How long will you all attack one man *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 10101 101 101 10101 101}
\FirstLetter{I}n God alone is my s\pointup{o}ul at rest;\Med\\
my help comes fr\pointup{o}m him.\\
He alone is my r\pointup{o}ck, my stronghold,\Med\\
my fortress: I st\pointup{a}nd firm.

How long will you all att\pointup{a}ck one man\Med\\
to break h\pointup{\i}m down,\\
as though he were a tott\pointup{e}ring wall,\Med\\
or a tumbl\pointup{\i}ng fence?

Their plan is only t\pointup{o} destroy:\Med\\
they take pleasure \pointup{\i}n lies.\\
With their mouth they \pointup{u}tter blessing\Med\\
but in their heart th\pointup{e}y curse.

In God alone be at r\pointup{e}st, my soul;\Med\\
for my hope comes fr\pointup{o}m him.\\
He alone is my r\pointup{o}ck, my stronghold,\Med\\
my fortress: I st\pointup{a}nd firm.

In God is my safet\pointup{y} and glory,\Med\\
the rock of \pointup{m}y strength.\\
Take refuge in God, \pointup{a}ll you people.\Med\\
Trust him at \pointup{a}ll times.\\
Pour out your h\pointup{e}arts before him\Med\\
for God is \pointup{o}ur refuge.

Common folk are onl\pointup{y} a breath,\Med\\
great men an \pointup{\i}llusion.\\
Placed in the sc\pointup{a}les, they rise;\Med\\
they weigh less than \pointup{a} breath.

Do not put your trust \pointup{\i}n oppression\Med\\
nor vain hopes \pointup{o}n plunder.\\
Do not set your h\pointup{e}art on riches\Med\\
even when they \pointup{\i}ncrease.

For God has said onl\pointup{y} one thing:\Med\\
only two do \pointup{I} know:\\
that to God alone b\pointup{e}longs power\Med\\
and to you, L\pointup{o}rd, love;\\
and that you rep\pointup{a}y each man\Med\\
according to h\pointup{\i}s deeds.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
