\settowidth{\versewidth}{and, by means of him, to reconcile everything in his person,}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{011 101 101 101 101 101 101}
\FirstLetter{L}et us give thanks to the F\pointup{a}ther\Flex\\
for having made y\pointup{o}u worthy\Med\\
to share the lot of the saints \pointup{\i}n light.

He rescued us from the power \pointup{o}f darkness\Med\\
and brought us into the kingdom of his belov\pointup{e}d Son.\\
Through him we have r\pointup{e}demption,\Med\\
the forgiveness of \pointup{o}ur sins.

He is the image of the invisibl\pointup{e} God,\Med\\
the first-born of \pointup{a}ll creatures.\\
In him everything in heaven and on earth was cr\pointup{e}ated,\Med\\
things visible and \pointup{\i}nvisible.

All were created thr\pointup{o}ugh him;\Med\\
all were created f\pointup{o}r him.\\
He is before all else th\pointup{a}t is.\Med\\
In him everything continues \pointup{\i}n being.

It is he who is head of the body, th\pointup{e} church!\Med\\
he who is the b\pointup{e}ginning,\\
the first-born of th\pointup{e} dead,\Med\\
so that primacy may be his \pointup{\i}n everything.

It pleased God to make absolute fullness reside \pointup{\i}n him\Med\\
and, by means of him, to reconcile everything in h\pointup{\i}s person,\\
both on earth and in th\pointup{e} heavens,\Med\\
making peace through the blood of h\pointup{\i}s cross.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
