\begin{verse}
  \begin{patverse}
    \indentpattern{0101 101 101 101 10101 101 101 10101 101}
\FirstLetter{I}n God alone is my soul \pointup{a}t rest;\Med\\
my help comes fr\pointup{o}m him.\\
He alone is my rock, m\pointup{y} stronghold,\Med\\
my fortress: I st\pointup{a}nd firm.

How long will you all attack \pointup{o}ne man\Med\\
to break h\pointup{\i}m down,\\
as though he were a totter\pointup{\i}ng wall,\Med\\
or a tumbl\pointup{\i}ng fence?

Their plan is only to d\pointup{e}stroy:\Med\\
they take pleasure \pointup{\i}n lies.\\
With their mouth they utt\pointup{e}r blessing\Med\\
but in their heart th\pointup{e}y curse.

In God alone be at rest, m\pointup{y} soul;\Med\\
for my hope comes fr\pointup{o}m him.\\
He alone is my rock, m\pointup{y} stronghold,\Med\\
my fortress: I st\pointup{a}nd firm.

In God is my safety \pointup{a}nd glory,\Med\\
the rock of \pointup{m}y strength.\\
Take refuge in God, all y\pointup{o}u people.\Med\\
Trust him at \pointup{a}ll times.\\
Pour out your hearts b\pointup{e}fore him\Med\\
for God is \pointup{o}ur refuge.

Common folk are only \pointup{a} breath,\Med\\
great men an \pointup{\i}llusion.\\
Placed in the scales, th\pointup{e}y rise;\Med\\
they weigh less than \pointup{a} breath.

Do not put your trust \pointup{\i}n oppression\Med\\
nor vain hopes \pointup{o}n plunder.\\
Do not set your heart \pointup{o}n riches\Med\\
even when they \pointup{\i}ncrease.

For God has said only \pointup{o}ne thing:\Med\\
only two do \pointup{I} know:\\
that to God alone b\pointup{e}longs power\Med\\
and to you, L\pointup{o}rd, love;\\
and that you repay \pointup{e}ach man\Med\\
according to h\pointup{\i}s deeds.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
