\settowidth{\versewidth}{We are filled with the blessings of your house, *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 1011 101 101 101 11 101 101}
\FirstLetter{T}o you our pr\pointup{a}ise is due\Med\\
in Zion, \pointup{O} God.\\
To you we p\pointup{a}y our vows,\Med\\
you who hear \pointup{o}ur prayer.

To you all fl\pointup{e}sh will come\Med\\
with its burden \pointup{o}f sin.\\
Too heavy for us, \pointup{o}ur offenses,\Med\\
but you wipe them \pointup{a}way.

Blessed is he whom you ch\pointup{o}ose and call\Med\\
to dwell in y\pointup{o}ur courts.\\
We are filled with the blessings \pointup{o}f your house,\Med\\
of your hol\pointup{y} temple.

You keep your pl\pointup{e}dge with wonders,\Med\\
O God \pointup{o}ur savior,\\
the hope of \pointup{a}ll the earth\Med\\
and of far dist\pointup{a}nt isles.

You uphold the mountains w\pointup{\i}th your strength,\Med\\
you are girded w\pointup{\i}th power.\\
You still the roaring of the s\pointup{e}as,\Flex\\
the roaring \pointup{o}f their waves,\Med\\
and the tumult of th\pointup{e} peoples.

The ends of the earth st\pointup{a}nd in awe\Med\\
at the sight of y\pointup{o}ur wonders.\\
The lands of sunr\pointup{\i}se and sunset\Med\\
you fill with y\pointup{o}ur joy.

You care for the earth, g\pointup{\i}ve it water;\Med\\
you fill it w\pointup{\i}th riches.\\
Your river in heav\pointup{e}n brims over\Med\\
to provide \pointup{\i}ts grain.

And thus you provide f\pointup{o}r the earth;\Med\\
you drench \pointup{\i}ts furrows;\\
you level it, soften \pointup{\i}t with showers;\Med\\
you bless \pointup{\i}ts growth.

You crown the year with your goodn\pointup{e}ss.\Flex\\
Abundance flows \pointup{\i}n your steps;\Med\\
in the pastures of the wilderness \pointup{\i}t flows.

The hills are gird\pointup{e}d with joy,\Med\\
the meadows covered w\pointup{\i}th flocks,\\
the valleys are d\pointup{e}cked with wheat.\Med\\
They shout for joy, yes th\pointup{e}y sing.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
