\settowidth{\versewidth}{Bearing in their hands their gifts for the King of heaven.}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01 11 11 11 1011 11 11 1 1 11 101}
\FirstLetter{L}et all men speak \pointup{o}f his majesty,\Med\\
and sing his praises in J\pointup{e}rusalem.

O Jerusalem, holy cit\pointup{y},\Flex\\
he scourged you for the works \pointup{o}f your hands,\Med\\
but will again pity the children of th\pointup{e} righteous.

Praise the Lord for his goodn\pointup{e}ss,\Flex\\
and bless the King \pointup{o}f the ages,\Med\\
so that his tent may be rebuilt in you w\pointup{\i}th joy.

May he gladden within you all who were capt\pointup{\i}ves;\Flex\\
all who were ravaged may he cher\pointup{\i}sh within you\Med\\
for all generations t\pointup{o} come.

A bright light will shine to all parts \pointup{o}f the earth;\Med\\
many nations shall come to you from \pointup{a}far,\\
and the inhabitants of all the limits of the \pointup{e}arth,\Flex\\
drawn to you by the name of th\pointup{e} Lord God,\Med\\
Bearing in their hands their gifts for the King \pointup{o}f heaven.

Every generation shall give joyful praise in y\pointup{o}u,\Flex\\
and shall call you the ch\pointup{o}sen one,\Med\\
through all ages f\pointup{o}rever.

Go, then, rejoice over the children of the right\pointup{e}ous,\Flex\\
who shall all be gath\pointup{e}red together\Med\\
and shall bless the Lord of th\pointup{e} ages.

Happy are th\pointup{o}se who love you,\Med\\
and happy those who rejoice in your pr\pointup{o}sperity.

Happy are all who shall grieve \pointup{o}ver you,\Med\\
over all your ch\pointup{a}stisements,

for they shall rejoice in y\pointup{o}u\Flex\\
as they behold all your j\pointup{o}y forever.\Med\\
My spirit blesses the Lord, the gr\pointup{e}at King.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be for ever. \pointupl{A}men.

  \end{patverse}
\end{verse}
