\settowidth{\versewidth}{He knows that wise men and fools must both perish *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 1011 1011 1 101}
\FirstLetter{H}ear this, all y\pointup{o}u peoples,\Med\\
give heed, all who dwell \pointup{\i}n the world,\\
men both low \pointup{a}nd high,\Med\\
rich and p\pointup{o}or alike!

My lips will speak words \pointup{o}f wisdom.\Med\\
My heart is f\pointup{u}ll of insight.\\
I will turn my mind to \pointup{a} parable,\Med\\
with the harp I will s\pointup{o}lve my problem.

Why should I fear in ev\pointup{\i}l days\Med\\
the malice of the foes wh\pointup{o} surround me,\\
men who trust in th\pointup{e}ir wealth,\Med\\
and boast of the vastness \pointup{o}f their riches?

For no man can buy his \pointup{o}wn ransom,\Med\\
or pay a price to God f\pointup{o}r his life.\\
The ransom of his soul is beyond h\pointup{\i}m.\Flex\\
He cannot buy life with\pointup{o}ut end,\Med\\
nor avoid coming t\pointup{o} the grave.

He knows that wise men and fools must b\pointup{o}th perish\Med\\
and leave their w\pointup{e}alth to others.\\
Their graves are their homes for ev\pointup{e}r,\Flex\\
their dwelling place from age t\pointup{o} age,\Med\\
though their names spread wide thr\pointup{o}ugh the land.

In his riches, man l\pointup{a}cks wisdom:\Med\\
he is like the beasts that \pointup{a}re destroyed.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the H\pointup{o}ly Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forev\pointup{e}r. Amen. 
  \end{patverse}
\end{psalmverse}
