\begin{verse}
  \begin{patverse}
    \indentpattern{0101 101 101 1011 101 1011 101 101 101 101}
\FirstLetter{N}ot to us, Lord, not t\pointup{o} us,\Med\\
but to your name give th\pointup{e} glory\\
for the sake of your love and y\pointup{o}ur truth,\Med\\
lest the heathen say: “Where is th\pointup{e}ir God?”

But our God is in th\pointup{e} heavens;\Med\\
he does whatever h\pointup{e} wills.\\
Their idols are silver \pointup{a}nd gold,\Med\\
the work of hum\pointup{a}n hands.

They have mouths but they can\pointup{n}ot speak;\Med\\
they have eyes but they cann\pointup{o}t see;\\
they have ears but they cann\pointup{o}t hear;\Med\\
they have nostrils but they cann\pointup{o}t smell.

With their hands they cann\pointup{o}t feel;\Flex\\
with their feet they cann\pointup{o}t walk.\Med\\
No sound comes from their thr\pointup{o}ats.\\
Their makers will come to be l\pointup{\i}ke them\Med\\
and so will all who trust \pointup{\i}n them.

Sons of Israel, trust in th\pointup{e} Lord;\Med\\
he is their help and th\pointup{e}ir shield\\
Sons of Aaron, trust in th\pointup{e} Lord;\Med\\
he is their help and th\pointup{e}ir shield.

You who fear him, trust in th\pointup{e} Lord;\Med\\
he is their help and th\pointup{e}ir shield.\\
He remembers us, and he will bless \pointup{u}s;\Flex\\
he will bless the sons \pointup{o}f Israel.\Med\\
He will bless the sons \pointup{o}f Aaron.

The Lord will bless those wh\pointup{o} fear him,\Med\\
the little no less than th\pointup{e} great:\\
to you may the Lord gr\pointup{a}nt increase,\Med\\
to you and all y\pointup{o}ur children.

May you be blessed by th\pointup{e} Lord,\Med\\
the maker of heaven \pointup{a}nd earth.\\
The heavens belong to th\pointup{e} Lord\Med\\
but the earth he has given t\pointup{o} men.

The dead shall not praise th\pointup{e} Lord,\Med\\
nor those who go down into th\pointup{e} silence.\\
But we who live bless th\pointup{e} Lord\Med\\
now and for ever. \pointupl{A}men.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
