\settowidth{\versewidth}{From his holy place God has made this promise; +}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01011 10101 1011 10101 101 101 101}
\FirstLetter{M}y heart is ready, \pointup{O} God;\Med\\
I will sing, sing y\pointup{o}ur praise.\\
Awake, my s\pointup{o}ul;\Flex\\
awake, lyre \pointup{a}nd harp,\Med\\
I will awake th\pointup{e} dawn.

I will thank you, Lord, among th\pointup{e} peoples,\Med\\
among the nations I w\pointup{\i}ll praise you,\\
for your love reaches to th\pointup{e} heavens\Med\\
and your truth to th\pointup{e} skies.\\
O God, arise above th\pointup{e} heavens;\Med\\
may your glory shine \pointup{o}n earth!

O come and deliver y\pointup{o}ur friends;\Med\\
help with your right hand and r\pointup{e}ply.\\
From his holy place God has made this prom\pointup{\i}se;\Flex\\
‘I will triumph and divide the land \pointup{o}f Shechem,\\
I will measure out the valley \pointup{o}f Succoth.

Gilead is mine and M\pointup{a}nasseh,\Med\\
Ephraim I take for m\pointup{y} helmet,\\
Judah for my command\pointup{e}r’s staff.\Med\\
Moab I will use for m\pointup{y} washbowl,\\
on Edom I will plant m\pointup{y} shoe.\Med\\
Over the Philistines I will shout \pointup{\i}n triumph.’

But who will lead me to conquer th\pointup{e} fortress?\Med\\
Who will bring me face to face w\pointup{\i}th Edom?\\
Will you utterly reject us, \pointup{O} God,\Med\\
and no longer march with \pointup{o}ur armies?

Give us help against th\pointup{e} foe,\Med\\
for the help of man \pointup{\i}s vain.\\
With God we shall d\pointup{o} bravely\Med\\
and he will trample down \pointup{o}ur foes.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be for ever. \pointupl{A}men.
  \end{patverse}
  \end{psalmverse}
