\settowidth{\versewidth}{I will thank you, Lord, among the peoples, *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 1011 101 1 101 11011 101 1 101}
    \FirstLetter{H}ave mercy on me, G\pointup{o}d, have mercy\Med\\
for in you my soul has tak\pointup{e}n refuge.\\
In the shadow of your wings \pointup{I} take refuge\Med\\
till the storms of destruction p\pointup{a}ss by.

I call to you God th\pointup{e} Most High,\Med\\
to you who have always been m\pointup{y} help.\\
May you send from heaven and save m\pointup{e}\Flex\\
and shame those wh\pointup{o} assail me.\Med\\
May God send his truth and h\pointup{\i}s love.

My soul lies down \pointup{a}mong lions,\Med\\
who would devour the sons \pointup{o}f men.\\
Their teeth are \pointup{s}pears and arrows,\Med\\
their tongue a sharp\pointup{e}ned sword.

O God, arise ab\pointup{o}ve the heavens;\Med\\
may your glory shine \pointup{o}n earth!

They laid a snare f\pointup{o}r my steps\Med\\
my soul was b\pointup{o}wed down.\\
They dug a pit \pointup{\i}n my path\Med\\
but fell in it th\pointup{e}mselves.

My heart is ready, O G\pointup{o}d,\Flex\\
my h\pointup{e}art is ready.\Med\\
I will sing, I will sing y\pointup{o}ur praise.\\
Awake, my s\pointup{o}ul;\Flex\\
awake, l\pointup{y}re and harp,\Med\\
I will awake th\pointup{e} dawn.

I will thank you, Lord, am\pointup{o}ng the peoples,\Med\\
among the nations I w\pointup{\i}ll praise you\\
for your love reaches t\pointup{o} the heavens\Med\\
and your truth to th\pointup{e} skies.

O God, arise ab\pointup{o}ve the heavens;\Med\\
may your glory shine \pointup{o}n earth.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
