\settowidth{\versewidth}{From the country of Jordan and Mount Hermon}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 10101 101 101 101 101 101 101 101 101}
\FirstLetter{L}ike the deer th\pointup{a}t yearns\Med\\
for runn\pointup{\i}ng streams,\\
so my soul \pointup{\i}s yearning\Med\\
for you, m\pointup{y} God.

My soul is thirsting f\pointup{o}r God,\Med\\
the God of m\pointup{y} life;\\
when can I enter \pointup{a}nd see\Med\\
the face \pointup{o}f God?

My tears have become m\pointup{y} bread,\Med\\
by night, b\pointup{y} day,\\
as I hear it said all the d\pointup{a}y long:\Med\\
“Where is y\pointup{o}ur God?”

These things will I r\pointup{e}member\Med\\
as I pour out m\pointup{y} soul:\\
how I would lead the rejoic\pointup{\i}ng crowd\Med\\
into the house \pointup{o}f God,\\
amid cries of gladness and th\pointup{a}nksgiving,\Med\\
the throng wild w\pointup{\i}th joy.

Why are you cast down, m\pointup{y} soul,\Med\\
why groan w\pointup{\i}thin me?\\
Hope in God; I will praise h\pointup{\i}m still,\Med\\
my savior and m\pointup{y} God.

My soul is cast down w\pointup{\i}thin me\Med\\
as I think \pointup{o}f you,\\
from the country of Jordan and M\pointup{o}unt Hermon,\Med\\
from the Hill \pointup{o}f Mizar.

Deep is calling \pointup{o}n deep,\Med\\
in the roar of th\pointup{e} waters;\\
your torrents and all y\pointup{o}ur waves\Med\\
swept ov\pointup{e}r me.

By day the Lord w\pointup{\i}ll send\Med\\
his lov\pointup{\i}ng kindness;\\
by night I will sing t\pointup{o} him,\Med\\
praise the God of m\pointup{y} life.

I will say to God, m\pointup{y} rock:\Med\\
“Why have you f\pointup{o}rgotten me?\\
Why do I g\pointup{o} mourning\Med\\
oppressed by th\pointup{e} foe?”

With cries that pierce me to m\pointup{y} heart,\Med\\
my enemies r\pointup{e}vile me,\\
saying to me all the d\pointup{a}y long:\Med\\
“Where is y\pointup{o}ur God?”

Why are you cast down, m\pointup{y} soul,\Med\\
why groan w\pointup{\i}thin me?\\
Hope in God; I will praise h\pointup{\i}m still,\Med\\
my savior and m\pointup{y} God.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
