\settowidth{\versewidth}{They are happy, whose strength is in you, *}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{01 101 101 101 1101 101 101 101 1 101}
\FirstLetter{H}ow lovely is your dw\pointup{e}lling place,\Med\\
Lord, G\pointup{o}d of hosts.

My soul is long\pointup{\i}ng and yearning,\Med\\
is yearning for the courts \pointup{o}f the Lord.\\
My heart and my soul ring \pointup{o}ut their joy\Med\\
to God, the l\pointup{\i}ving God.

The sparrow herself f\pointup{\i}nds a home\Med\\
and the swallow a nest f\pointup{o}r her brood;\\
she lays her young b\pointup{y} your altars,\Med\\
Lord of hosts, my king \pointup{a}nd my God.

They are happy, who dwell \pointup{\i}n your house,\Med\\
for ever sing\pointup{\i}ng your praise.\\
They are happy, whose strength \pointup{\i}s in you,\Med\\
in whose hearts are the r\pointup{o}ads to Zion.

As they go through the Bitter V\pointup{a}lley\Flex\\
they make it a pl\pointup{a}ce of springs\Med\\
the autumn rain covers \pointup{\i}t with blessings.\\
They walk with ever gr\pointup{o}wing strength,\Med\\
they will see the God of g\pointup{o}ds in Zion.

O Lord God of hosts, h\pointup{e}ar my prayer,\Med\\
give ear, O G\pointup{o}d of Jacob.\\
Turn your eyes, O G\pointup{o}d, our shield,\Med\\
look on the face of y\pointup{o}ur anointed.

One day with\pointup{\i}n your courts\Med\\
is better than a thous\pointup{a}nd elsewhere.\\
The threshold of the h\pointup{o}use of God\Med\\
I prefer to the dwellings \pointup{o}f the wicked.

For the Lord God is a ramp\pointup{a}rt, a shield;\Med\\
he will give us his fav\pointup{o}r and glory.\\
The Lord will not refuse \pointup{a}ny good\Med\\
to those who walk w\pointup{\i}thout blame.

Lord, G\pointup{o}d of hosts,\Med\\
happy the man who tr\pointup{u}sts in you!

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the H\pointup{o}ly Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forev\pointup{e}r. Amen. 
  \end{patverse}
\end{verse}
