\settowidth{\versewidth}{I shall not die, I shall live and recount his deeds.}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{01 10101 10101 101 101011 10101 10101 10101 10101 10101 10101 101}
    \FirstLetter{G}ive thanks to the Lord for he \pointup{\i}s good,\Med\\
    for his love end\pointup{u}res for ever.

    Let the sons of Isra\pointup{e}l say:\Med\\
    “His love end\pointup{u}res for ever.”\\
    Let the sons of Aar\pointup{o}n say:\Med\\
    “His love end\pointup{u}res for ever.”\\
    Let those who fear the L\pointup{o}rd say:\Med\\
    “His love end\pointup{u}res for ever.”

    I called to the Lord in my d\pointup{\i}stress;\Med\\
    he answ\pointup{e}red and freed me.\\
    The Lord is at my side; I do n\pointup{o}t fear.\Med\\
    what can man d\pointup{o} against me?\\
    The Lord is at my side as m\pointup{y} helper;\Med\\
    I shall look down \pointup{o}n my foes.

    It is better to take refuge in th\pointup{e} Lord\Med\\
    than to tr\pointup{u}st in men;\\
    it is better to take refuge in th\pointup{e} Lord\Med\\
    than to tr\pointup{u}st in princes.

    The nations all \pointup{e}ncompassed me;\Med\\
    in the Lord’s n\pointup{a}me I crushed them.\\
    They compassed me, compassed m\pointup{e} about;\Med\\
    in the Lord’s n\pointup{a}me I crushed them.\\
    They compassed me about like b\pointup{e}es;\Flex\\
    they blazed like a fire am\pointup{o}ng thorns.\Med\\
    In the Lord’s n\pointup{a}me I crushed them.

    I was hard-pressed and w\pointup{a}s falling\Med\\
    but the Lord c\pointup{a}me to help me.\\
    The Lord is my strength and m\pointup{y} song;\Med\\
    he \pointup{\i}s my savior.\\
    There are shouts of joy \pointup{a}nd victory\Med\\
    in the tents \pointup{o}f the just.

    The Lord’s right hand h\pointup{a}s triumphed;\Med\\
    his r\pointup{\i}ght hand raised me.\\
    The Lord’s right hand h\pointup{a}s triumphed;\Med\\
    I shall not die, I shall live and rec\pointup{o}unt his deeds.\\
    I was punished, I was punished by th\pointup{e} Lord,\Med\\
    but not d\pointup{o}omed to die.

    Open to me the gates \pointup{o}f holiness:\Med\\
    I will enter \pointup{a}nd give thanks.\\
    This is the Lord’s \pointup{o}wn gate\Med\\
    where the j\pointup{u}st may enter.\\
    I will thank you for you h\pointup{a}ve answered\Med\\
    and you \pointup{a}re my savior.

    The stone which the builders r\pointup{e}jected\Med\\
    has become the c\pointup{o}rner stone.\\
    This is the work of th\pointup{e} Lord,\Med\\
    a marvel \pointup{\i}n our eyes.\\
    This day was made by th\pointup{e} Lord;\Med\\
    we rejoice \pointup{a}nd are glad.

    O Lord, grant us s\pointup{a}lvation;\Med\\
    O Lord, gr\pointup{a}nt success.\\
    Blessed in the name of th\pointup{e} Lord\Med\\
    is h\pointup{e} who comes.\\
    We bless you from the house of th\pointup{e} Lord;\Med\\
    the Lord God \pointup{\i}s our light.

    Go forward in procession w\pointup{\i}th branches\Med\\
    even t\pointup{o} the altar.\\
    You are my God, \pointup{I} thank you.\Med\\
    My G\pointup{o}d, I praise you.\\
    Give thanks to the Lord for he \pointup{\i}s good;\Med\\
    for his love end\pointup{u}res for ever.

    Glory to the Father and to th\pointup{e} Son,\Med\\
    and to the H\pointup{o}ly Spirit:\\
    as it was in the beginning, \pointup{\i}s now,\Med\\
    and will be forev\pointup{e}r. Amen.
  \end{patverse}
\end{verse}
