\settowidth{\versewidth}{so I left them in their stubbornness of heart *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01 101 101 101 101 1011 101 101 101 101}
\FirstLetter{R}ing out your joy to God \pointup{o}ur strength,\Med\\
shout in triumph to the God \pointup{o}f Jacob.

Raise a song and sound th\pointup{e} timbrel,\Med\\
the sweet-sounding harp and th\pointup{e} lute;\\
blow the trumpet at th\pointup{e} new moon,\Med\\
when the moon is full, on \pointup{o}ur feast.

For this is Isra\pointup{e}l’s law,\Med\\
a command of the God \pointup{o}f Jacob.\\
He imposed it as a rule \pointup{o}n Joseph,\Med\\
when he went out against the land \pointup{o}f Egypt.

A voice I did not know said t\pointup{o} me:\Med\\
“I freed your shoulder from th\pointup{e} burden;\\
your hands were freed from th\pointup{e} load.\Med\\
You called in distress and \pointup{I} saved you.

I answered, concealed in th\pointup{e} storm cloud;\Med\\
at the waters of Meribah I test\pointup{e}d you.\\
Listen, my people, to m\pointup{y} warning.\Med\\
O Israel, if only you w\pointup{o}uld heed!

Let there be no foreign god \pointup{a}mong you.\Med\\
no worship of an ali\pointup{e}n god.\\
I am the Lord your G\pointup{o}d,\Flex\\
who brought you from the land \pointup{o}f Egypt.\Med\\
Open wide your mouth and I w\pointup{\i}ll fill it.

But my people did not heed m\pointup{y} voice\Med\\
and Israel would not \pointup{o}bey,\\
so I left them in their stubbornness \pointup{o}f heart\Med\\
to follow their own d\pointup{e}signs.

O that my people w\pointup{o}uld heed me,\Med\\
that Israel would walk in m\pointup{y} ways!\\
At once I would subdue th\pointup{e}ir foes,\Med\\
turn my hand against th\pointup{e}ir enemies.

The Lord’s enemies would cringe at th\pointup{e}ir feet\Med\\
and their subjection would last f\pointup{o}r ever.\\
But Israel I would feed with fin\pointup{e}st wheat\Med\\
and fill them with honey from th\pointup{e} rock.”

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
