\settowidth{\versewidth}{He knows that wise men and fools must both perish *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 1011 1011 1 101}
\FirstLetter{H}ear this, all y\pointup{o}u peoples,\Med\\
give heed, all who dwell in th\pointup{e} world,\\
men both low \pointup{a}nd high,\Med\\
rich and poor \pointup{a}like!

My lips will speak words \pointup{o}f wisdom.\Med\\
My heart is full \pointup{o}f insight.\\
I will turn my mind to \pointup{a} parable,\Med\\
with the harp I will solve m\pointup{y} problem.

Why should I fear in ev\pointup{\i}l days\Med\\
the malice of the foes who s\pointup{u}rround me,\\
men who trust in th\pointup{e}ir wealth,\Med\\
and boast of the vastness of th\pointup{e}ir riches?

For no man can buy his \pointup{o}wn ransom,\Med\\
or pay a price to God for h\pointup{\i}s life.\\
The ransom of his soul is beyond h\pointup{\i}m.\Flex\\
He cannot buy life with\pointup{o}ut end,\Med\\
nor avoid coming to th\pointup{e} grave.

He knows that wise men and fools must b\pointup{o}th perish\Med\\
and leave their wealth t\pointup{o} others.\\
Their graves are their homes for ev\pointup{e}r,\Flex\\
their dwelling place from age t\pointup{o} age,\Med\\
though their names spread wide through th\pointup{e} land.

In his riches, man l\pointup{a}cks wisdom:\Med\\
he is like the beasts that are d\pointup{e}stroyed.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
