\settowidth{\versewidth}{That you may be justified when you give sentence *}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 101 101 101 101 101 101}
    \FirstLetter{H}ave mercy on me, God, in your k\pointup{\i}ndness.\Med\\
In your compassion blot out my off\pointup{e}nse.\\
O wash me more and more from m\pointup{y} guilt\Med\\
and cleanse me from my s\pointup{\i}n.

My offenses truly \pointup{I} know them;\Med\\
my sin is always bef\pointup{o}re me\\
Against you, you alone, have \pointup{I} sinned;\Med\\
what is evil in your sight I have d\pointup{o}ne.

That you may be justified when you g\pointup{\i}ve sentence\Med\\
and be without reproach when you j\pointup{u}dge.\\
O see, in guilt I w\pointup{a}s born,\Med\\
a sinner was I conc\pointup{e}ived.

Indeed you love truth in th\pointup{e} heart;\Med\\
then in the secret of my heart teach me w\pointup{\i}sdom.\\
O purify me, then I shall b\pointup{e} clean;\Med\\
O wash me, I shall be whiter than sn\pointup{o}w.

Make me hear rejoicing \pointup{a}nd gladness,\Med\\
that the bones you have crushed may rev\pointup{\i}ve.\\
From my sins turn away y\pointup{o}ur face\Med\\
and blot out all my g\pointup{u}ilt.

A pure heart create for me, \pointup{O} God,\Med\\
put a steadfast spirit with\pointup{\i}n me.\\
Do not cast me away from y\pointup{o}ur presence,\Med\\
nor deprive me of your holy sp\pointup{\i}rit.

Give me again the joy of y\pointup{o}ur help;\Med\\
with a spirit of fervor sust\pointup{a}in me,\\
that I may teach transgressors y\pointup{o}ur ways\Med\\
and sinners may return to y\pointup{o}u.

O rescue me, God, m\pointup{y} helper,\Med\\
and my tongue shall ring out your g\pointup{o}odness.\\
O Lord, open m\pointup{y} lips\Med\\
and my mouth shall declare your pr\pointup{a}ise.

For in sacrifice you take no d\pointup{e}light,\Med\\
burnt offering from me you would ref\pointup{u}se,\\
my sacrifice, a contr\pointup{\i}te spirit,\Med\\
a humbled, contrite heart you will not sp\pointup{u}rn.

In your goodness, show favor t\pointup{o} Zion:\Med\\
rebuild the walls of Jer\pointup{u}salem.\\
Then you will be pleased with lawf\pointup{u}l sacrifice,\Med\\
holocausts offered on your \pointup{a}ltar.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Holy Sp\pointup{\i}rit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. Am\pointup{e}n.
  \end{patverse}
\end{verse}
