\settowidth{\versewidth}{will guard him, give him life, make him happy in the land *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{010101 10101 10101 10101 1 101}
\FirstLetter{H}appy the man who considers the poor \pointup{a}nd the weak.\Med\\
The Lord will save him in the day \pointup{o}f evil,\\
will guard him, give him life, make him happy \pointup{\i}n the land\Med\\
and will not give him up to the will of h\pointup{\i}s foes.\\
The Lord will help him on his b\pointup{e}d of pain,\Med\\
he will bring him back from sickness t\pointup{o} health.

As for me, I said: “Lord, have merc\pointup{y} on me,\Med\\
heal my soul for I have sinned \pointup{a}gainst you.”\\
My foes are speaking ev\pointup{\i}l against me.\Med\\
“how long before he dies and his name be f\pointup{o}rgotten?”\\
They come to visit me and speak \pointup{e}mpty words,\Med\\
their hearts full of malice, they spread it \pointup{a}broad.

My enemies whisper togeth\pointup{e}r against me.\Med\\
They all weigh up the evil which \pointup{\i}s on me.\\
“Some deadly thing has fast\pointup{e}ned upon him,\Med\\
he will not rise again from where h\pointup{e} lies.”\\
Thus even my friend, in wh\pointup{o}m I trusted,\Med\\
who ate my bread, has turned \pointup{a}gainst me.

But you, O Lord, have merc\pointup{y} on me.\Med\\
Let me rise once more and I will r\pointup{e}pay them.\\
By this I shall know that you \pointup{a}re my friend,\Med\\
if my foes do not shout in triumph ov\pointup{e}r me.\\
If you uphold me I shall b\pointup{e} unharmed\Med\\
and set in your presence for ev\pointup{e}r more.

Blessed be the Lord, the G\pointup{o}d of Israel\Med\\
from age to age. Amen. \pointupl{A}men.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
