\begin{verse}
  \begin{patverse}
    \indentpattern{011 1011 101 101 101 11 101}
\FirstLetter{P}reserve me, God, I take refuge in y\pointup{o}u.\Flex\\
I say to the Lord: “You are m\pointup{y} God.\Med\\
My happiness lies in you \pointup{a}lone.”

He has put into my heart a marvel\pointup{o}us love\Med\\
for the faithful ones who dwell in h\pointup{\i}s land.\\
Those who choose other gods increase their sorr\pointup{o}ws.\Flex\\
Never will I offer their offerings \pointup{o}f blood.\Med\\
Never will I take their name upon m\pointup{y} lips.

O Lord, it is you who are my portion \pointup{a}nd cup;\Med\\
it is you yourself who are m\pointup{y} prize.\\
The lot marked out for me is my d\pointup{e}light:\Med\\
welcome indeed the heritage that falls t\pointup{o} me!

I will bless the Lord who gives m\pointup{e} counsel,\Med\\
who even at night directs m\pointup{y} heart.\\
I keep the Lord ever in m\pointup{y} sight:\Med\\
since he is at my right hand, I shall st\pointup{a}nd firm.

And so my heart rejoices, my soul \pointup{\i}s glad;\Med\\
even my body shall rest \pointup{\i}n safety.\\
For you will not leave my soul among th\pointup{e} dead,\Med\\
nor let your beloved know d\pointup{e}cay.

You will show me the path of l\pointup{\i}fe,\Flex\\
the fullness of joy in y\pointup{o}ur presence,\Med\\
at your right hand happiness f\pointup{o}r ever.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
