\settowidth{\versewidth}{We are filled with the blessings of your house, *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 1011 101 101 101 11 101 101}
    \FirstLetter{T}o you our praise \pointup{\i}s due\Med\\
in Zion, \pointupl{O} God.\\
To you we pay \pointup{o}ur vows,\Med\\
you who hear \pointup{o}ur prayer.

To you all flesh w\pointup{\i}ll come\Med\\
with its burden \pointup{o}f sin.\\
Too heavy for us, \pointup{o}ur offenses,\Med\\
but you wipe them \pointup{a}way.

Blessed is he whom you choose \pointup{a}nd call\Med\\
to dwell in y\pointup{o}ur courts.\\
We are filled with the blessings of y\pointup{o}ur house,\Med\\
of your hol\pointup{y} temple.

You keep your pledge w\pointup{\i}th wonders,\Med\\
O God \pointup{o}ur savior,\\
the hope of all th\pointup{e} earth\Med\\
and of far dist\pointup{a}nt isles.

You uphold the mountains with y\pointup{o}ur strength,\Med\\
you are girded w\pointup{\i}th power.\\
You still the roaring of the s\pointup{e}as,\Flex\\
the roaring of th\pointup{e}ir waves,\Med\\
and the tumult of th\pointup{e} peoples.

The ends of the earth stand \pointup{\i}n awe\Med\\
at the sight of y\pointup{o}ur wonders.\\
The lands of sunrise \pointup{a}nd sunset\Med\\
you fill with y\pointup{o}ur joy.

You care for the earth, give \pointup{\i}t water;\Med\\
you fill it w\pointup{\i}th riches.\\
Your river in heaven br\pointup{\i}ms over\Med\\
to provide \pointup{\i}ts grain.

And thus you provide for th\pointup{e} earth;\Med\\
you drench \pointup{\i}ts furrows;\\
you level it, soften it w\pointup{\i}th showers;\Med\\
you bless \pointup{\i}ts growth.

You crown the year with your goodn\pointup{e}ss.\Flex\\
Abundance flows in y\pointup{o}ur steps;\Med\\
in the pastures of the wilderness \pointup{\i}t flows.

The hills are girded w\pointup{\i}th joy,\Med\\
the meadows covered w\pointup{\i}th flocks,\\
the valleys are decked w\pointup{\i}th wheat.\Med\\
They shout for joy, yes th\pointup{e}y sing.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
