\settowidth{\versewidth}{To both man and beast you give protection. *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 101 101 1 101}
    \FirstLetter{S}in speaks to th\pointup{e} sinner\Med\\
in the depths of h\pointup{\i}s heart.\\
There is no fear \pointup{o}f God\Med\\
before h\pointup{\i}s eyes.

He so flatters himself in h\pointup{\i}s mind\Med\\
that he knows not h\pointup{\i}s guilt.\\
In his mouth are mischief and d\pointup{e}ceit.\Med\\
All wisdom \pointup{\i}s gone.

He plots the defeat \pointup{o}f goodness\Med\\
as he lies on h\pointup{\i}s bed.\\
He has set his foot on ev\pointup{\i}l ways,\Med\\
he clings to what \pointup{\i}s evil.

Your love, Lord, reaches t\pointup{o} heaven;\Med\\
your truth to th\pointup{e} skies.\\
Your justice is like G\pointup{o}d’s mountain,\Med\\
your judgments like th\pointup{e} deep.

To both man and beast you give pr\pointup{o}tection.\Med\\
O Lord, how precious is y\pointup{o}ur love.\\
My God, the sons \pointup{o}f men\Med\\
find refuge in the shelter of y\pointup{o}ur wings.

They feast on the riches of y\pointup{o}ur house;\Med\\
they drink from the stream of your d\pointup{e}light.\\
In you is the source \pointup{o}f life\Med\\
and in your light we s\pointup{e}e light.

Keep on loving those wh\pointup{o} know you,\Med\\
doing justice for upr\pointup{\i}ght hearts.\\
Let the foot of the proud n\pointup{o}t crush me\Med\\
nor the hand of the wicked cast m\pointup{e} out.

See how the evildo\pointup{e}rs fall!\Med\\
Flung down, they shall never \pointup{a}rise.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
