\settowidth{\versewidth}{will guard him, give him life, make him happy in the land *}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{010101 10101 10101 10101 1 101}
\FirstLetter{H}appy the man who considers the poor and th\pointup{e} weak.\Med\\
The Lord will save him in the day of \pointup{e}vil,\\
will guard him, give him life, make him happy in th\pointup{e} land\Med\\
and will not give him up to the will of his f\pointup{o}es.\\
The Lord will help him on his bed \pointup{o}f pain,\Med\\
he will bring him back from sickness to h\pointup{e}alth.

As for me, I said: “Lord, have mercy \pointup{o}n me,\Med\\
heal my soul for I have sinned ag\pointup{a}inst you.”\\
My foes are speaking evil \pointup{a}gainst me.\Med\\
“how long before he dies and his name be forg\pointup{o}tten?”\Med\\
They come to visit me and speak empt\pointup{y} words,\\
their hearts full of malice, they spread it abr\pointup{o}ad.

My enemies whisper together \pointup{a}gainst me.\Med\\
They all weigh up the evil which is \pointup{o}n me.\\
“Some deadly thing has fastened \pointup{u}pon him,\Med\\
he will not rise again from where he l\pointup{\i}es.”\\
Thus even my friend, in whom \pointup{I} trusted,\Med\\
who ate my bread, has turned ag\pointup{a}inst me.

But you, O Lord, have mercy \pointup{o}n me.\Med\\
Let me rise once more and I will rep\pointup{a}y them.\\
By this I shall know that you are m\pointup{y} friend,\Med\\
if my foes do not shout in triumph over m\pointup{e}.\\
If you uphold me I shall be \pointup{u}nharmed\Med\\
and set in your presence for ever m\pointup{o}re.

Blessed be the Lord, the God \pointup{o}f Israel\Med\\
from age to age. Amen. Am\pointup{e}n.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Holy Sp\pointup{\i}rit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. Am\pointup{e}n. 
  \end{patverse}
\end{verse}
