\begin{verse}
  \begin{patverse}
    \indentpattern{01 101 101 101 1101 101 101 101 1 101}
\FirstLetter{H}ow lovely is your dw\pointup{e}lling place,\Med\\
Lord, God \pointup{o}f hosts.

My soul is long\pointup{\i}ng and yearning,\Med\\
is yearning for the courts of th\pointup{e} Lord.\\
My heart and my soul ring \pointup{o}ut their joy\Med\\
to God, the liv\pointup{\i}ng God.

The sparrow herself f\pointup{\i}nds a home\Med\\
and the swallow a nest for h\pointup{e}r brood;\\
she lays her young b\pointup{y} your altars,\Med\\
Lord of hosts, my king and m\pointup{y} God.

They are happy, who dwell \pointup{\i}n your house,\Med\\
for ever singing y\pointup{o}ur praise.\\
They are happy, whose strength \pointup{\i}s in you,\Med\\
in whose hearts are the roads t\pointup{o} Zion.

As they go through the Bitter V\pointup{a}lley\Flex\\
they make it a pl\pointup{a}ce of springs\Med\\
the autumn rain covers it w\pointup{\i}th blessings.\\
They walk with ever gr\pointup{o}wing strength,\Med\\
they will see the God of gods \pointup{\i}n Zion.

O Lord God of hosts, h\pointup{e}ar my prayer,\Med\\
give ear, O God \pointup{o}f Jacob.\\
Turn your eyes, O G\pointup{o}d, our shield,\Med\\
look on the face of your \pointup{a}nointed.

One day with\pointup{\i}n your courts\Med\\
is better than a thousand \pointup{e}lsewhere.\\
The threshold of the h\pointup{o}use of God\Med\\
I prefer to the dwellings of th\pointup{e} wicked.

For the Lord God is a ramp\pointup{a}rt, a shield;\Med\\
he will give us his favor \pointup{a}nd glory.\\
The Lord will not refuse \pointup{a}ny good\Med\\
to those who walk with\pointup{o}ut blame.

Lord, G\pointup{o}d of hosts,\Med\\
happy the man who trusts \pointup{\i}n you!

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
