\begin{psalmverse}
  \begin{patverse}
    \indentpattern{010101 11 11011 110101 101 101011 11 11 101 101 101}
    \FirstLetter{T}ruly with you God \pointup{\i}s hidden,\Med\\
the God of Israel, th\pointup{e} savior!\\
Those are put to shame and d\pointup{\i}sgrace\Med\\
who vent their anger \pointup{a}gainst him.\\
Those go in d\pointup{\i}sgrace\Med\\
who c\pointup{a}rve images.

Israel, you are saved by the Lord, saved forev\pointup{e}r!\Flex\\
You shall never be put to shame or d\pointup{\i}sgrace\Med\\
in fut\pointup{u}re ages.

For thus says the L\pointup{o}rd,\Flex\\
the creator of the heavens, who \pointup{\i}s God,\Med\\
the designer and maker of th\pointup{e} earth\\
who established \pointup{\i}t,\Flex\\
not creating it to be \pointup{a} waste,\Med\\
but designing it to b\pointup{e} lived in:

I am the Lord, and there is no oth\pointup{e}r.\Flex\\
I have not spoken fr\pointup{o}m hiding\Med\\
nor from some dark place of th\pointup{e} earth.\\
And I have not said to the descendants \pointup{o}f Jacob,\Med\\
“Look for me in an empt\pointup{y} waste.”\\
I, the Lord, prom\pointup{\i}se justice,\Med\\
I foretell what \pointup{\i}s right.

Come and assemble, gather t\pointup{o}gether,\Med\\
you fugitives from among th\pointup{e} Gentiles!\\
They are without knowledge who bear wood\pointup{e}n idols\Med\\
and pray to gods that cann\pointup{o}t save.

Come here and d\pointup{e}clare\Med\\
in counsel t\pointup{o}gether:\\
Who announced this from the b\pointup{e}ginning\Med\\
and foretold it from \pointup{o}f old?\\
Was it not I, the L\pointup{o}rd,\Flex\\
besides whom there is no oth\pointup{e}r God?\Med\\
There is no just and saving God b\pointup{u}t me.

Turn to me and be safe,\Flex\\
all you ends of th\pointup{e} earth,\Med\\
for I am God; there is n\pointup{o} other!

By myself I sw\pointup{e}ar,\Flex\\
uttering my just d\pointup{e}cree\Med\\
and my unalter\pointup{a}ble word:

To me every knee sh\pointup{a}ll bend;\Med\\
by me every tongue sh\pointup{a}ll swear,\\
saying, “Only in th\pointup{e} Lord\Med\\
are just deeds \pointup{a}nd power.

“Before him in shame sh\pointup{a}ll come\Med\\
all who vent their anger \pointup{a}gainst him.\\
In the Lord shall be the vindication and th\pointup{e} glory\Med\\
of all the descendants \pointup{o}f Israel.”

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{psalmverse}
