\settowidth{\versewidth}{I shall not die, I shall live and recount his deeds.}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01 10101 10101 101 101011 10101 10101 10101 10101 10101 10101 101}
    \FirstLetter{G}ive thanks to the Lord for he \pointup{\i}s good,\Med\\
    for his love endures f\pointup{o}r ever.

    Let the sons of Isra\pointup{e}l say:\Med\\
    “His love endures f\pointup{o}r ever.”\\
    Let the sons of Aar\pointup{o}n say:\Med\\
    “His love endures f\pointup{o}r ever.”\\
    Let those who fear the L\pointup{o}rd say:\Med\\
    “His love endures f\pointup{o}r ever.”

    I called to the Lord in my d\pointup{\i}stress;\Med\\
    he answered \pointup{a}nd freed me.\\
    The Lord is at my side; I do n\pointup{o}t fear.\Med\\
    what can man do \pointup{a}gainst me?\\
    The Lord is at my side as m\pointup{y} helper;\Med\\
    I shall look down on m\pointup{y} foes.

    It is better to take refuge in th\pointup{e} Lord\Med\\
    than to trust \pointup{\i}n men;\\
    it is better to take refuge in th\pointup{e} Lord\Med\\
    than to trust \pointup{\i}n princes.

    The nations all \pointup{e}ncompassed me;\Med\\
    in the Lord’s name \pointup{I} crushed them.\\
    They compassed me, compassed m\pointup{e} about;\Med\\
    in the Lord’s name \pointup{I} crushed them.\\
    They compassed me about like b\pointup{e}es;\Flex\\
    they blazed like a fire am\pointup{o}ng thorns.\Med\\
    In the Lord’s name \pointup{I} crushed them.

    I was hard-pressed and w\pointup{a}s falling\Med\\
    but the Lord came t\pointup{o} help me.\\
    The Lord is my strength and m\pointup{y} song;\Med\\
    he is m\pointup{y} savior.\\
    There are shouts of joy \pointup{a}nd victory\Med\\
    in the tents of th\pointup{e} just.

    The Lord’s right hand h\pointup{a}s triumphed;\Med\\
    his right h\pointup{a}nd raised me.\\
    The Lord’s right hand h\pointup{a}s triumphed;\Med\\
    I shall not die, I shall live and recount h\pointup{\i}s deeds.\\
    I was punished, I was punished by th\pointup{e} Lord,\Med\\
    but not doomed t\pointup{o} die.

    Open to me the gates \pointup{o}f holiness:\Med\\
    I will enter and g\pointup{\i}ve thanks.\\
    This is the Lord’s \pointup{o}wn gate\Med\\
    where the just m\pointup{a}y enter.\\
    I will thank you for you h\pointup{a}ve answered\Med\\
    and you are m\pointup{y} savior.

    The stone which the builders r\pointup{e}jected\Med\\
    has become the corn\pointup{e}r stone.\\
    This is the work of th\pointup{e} Lord,\Med\\
    a marvel in \pointup{o}ur eyes.\\
    This day was made by th\pointup{e} Lord;\Med\\
    we rejoice and \pointup{a}re glad.

    O Lord, grant us s\pointup{a}lvation;\Med\\
    O Lord, grant s\pointup{u}ccess.\\
    Blessed in the name of th\pointup{e} Lord\Med\\
    is he wh\pointup{o} comes.\\
    We bless you from the house of th\pointup{e} Lord;\Med\\
    the Lord God is \pointup{o}ur light.

    Go forward in procession w\pointup{\i}th branches\Med\\
    even to th\pointup{e} altar.\\
    You are my God, \pointup{I} thank you.\Med\\
    My God, \pointup{I} praise you.\\
    Give thanks to the Lord for he \pointup{\i}s good;\Med\\
    for his love endures f\pointup{o}r ever.

    Glory to the Father and to th\pointup{e} Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
    as it was in the beginning, \pointup{\i}s now,\Med\\
    and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
