\documentclass[12pt,twocolumn,letterpaper]{book}
\usepackage[margin=0.4in,papersize={8.32in, 10.82in}]{geometry}
\usepackage{libertine}
\usepackage{lettrine}
\usepackage{verse}
\usepackage[compact]{titlesec}
\titleformat{\chapter}[display]
  {\normalfont\sffamily\filcenter}
  {\chaptertitlename\ \thechapter}{0pt}{\LARGE}

\titleformat{\section}
  {\normalfont\sffamily\large\bfseries\filcenter}
  {\thesection}{1em}{{\titlerule\vspace{1ex}}}

\titleformat{\subsection}
  {\normalfont\sffamily\bfseries}
  {\thesection}{1em}{}

\titleformat{\subsubsection}
  {\normalfont\filcenter\itshape\bfseries}
  {\thesection}{1em}{}
  
%% \titlespacing*{⟨command ⟩}{⟨left⟩}{⟨before-sep⟩}{⟨after-sep⟩}[⟨right-sep⟩]
\titlespacing*{\chapter}{0pt}{0pt}{10pt}
\titlespacing*{\section}{0pt}{20pt}{4pt}
\titlespacing*{\subsection}{0pt}{3ex}{1ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{1ex}
\titlespacing*{\paragraph}{0ex}{1ex}{1ex}[0ex]


\usepackage{fancyhdr}
\fancypagestyle{plain}{\fancyhf{}}
\pagestyle{empty}
\raggedright

\begin{document}
\chapter*{Daytime Prayer --- Friday, Week I}
\subsection*{HYMN}

\begin{verse}
O mighty Ruler, God of truth,\\
for days and seasons setting bounds,\\
you clothe with splendor morning light\\
and midday skies with brilliant heat.

Extinguish flames of bitter strife,\\
all harmful passion take away,\\
grant health unto our mortal frame,\\
and on our hearts bestow true peace.

Most loving Father, hear our prayer,\\
and you, O Christ coequal Son,\\
who with the Spirit Paraclete\\
now reign for all eternity. Amen.
\end{verse}

\footnotesize

Text: \emph{Rector potens, verax Deus,} attributed to St.~Ambrose, 340--397, © 2023 ICEL

\normalsize

\subsection*{PSALMODY}

\paragraph{Ant.\ 1}{Lightly I run in the way you have shown, for you have opened my heart to receive your law.}

\subsubsection*{Psalm 119:25--32}
\begin{verse}
My soul lies in the dust;~*\\
by your word revive me.\\
I declared my ways and you answered:~*\\
teach me your statutes.

Make me grasp the way of your precepts~*\\
and I will muse on your wonders.\\
My soul pines away with grief;~*\\
by your word raise me up.

Keep me from the way of error~*\\
and teach me your law.\\
I have chosen the way of truth~*\\
with your decrees before me.

I bind myself to do your will;~*\\
Lord, do not disappoint me.\\
I will run the way of your commands;~*\\
you give freedom to my heart.

Glory to the Father, and to the Son~*\\
and to the Holy Spirit:\\
as it was in the beginning, is now,~*\\
and will be for ever. Amen.
\end{verse}

\paragraph{Ant.}{Lightly I run in the way you have shown, for you have opened my heart to receive your law.}

\paragraph{Ant.\ 2}{I trust in the Lord and will not be shaken.}

\subsubsection*{Psalm 26}

\begin{verse}
Give judgment for me, O Lord: †\\
for I walk the path of perfection.~*\\
I trust in the Lord; I have not wavered.

Examine me, Lord, and try me;~*\\
O test my heart and my mind,\\
for your love is before my eyes~*\\
and I walk according to your truth.

I never take my place with liars~*\\
and with hypocrites I shall not go.\\
I hate the evil-doer’s company:~*\\
I will not take my place with the wicked.

To prove my innocence I wash my hands~*\\
and take my place around your altar,\\
singing a song of thanksgiving,~*\\
proclaiming all your wonders.

O Lord, I love the house where you dwell,~*\\
the place where your glory abides.

Do not sweep me away with sinners,~*\\
nor my life with bloodthirsty men\\
in whose hands are evil plots,~*\\
whose right hands are filled with gold.

As for me, I walk the path of perfection.~*\\
Redeem me and show me your mercy.\\
My foot stands on level ground:~*\\
I will bless the Lord in the assembly.

Glory to the Father, and to the Son~*\\
and to the Holy Spirit:\\
as it was in the beginning, is now,~*\\
and will be for ever. Amen.
\end{verse}

\paragraph{Ant.}{I trust in the Lord and will not be shaken.}

\paragraph{Ant.\ 3}{I put all my trust in the Lord, and he has not failed me.}

\subsubsection*{Psalm 28:1--3, 6--9}

\begin{verse}
To you, O Lord, I call,~*\\
my rock, hear me.\\
If you do not heed I shall become~*\\
like those in the grave.

Hear the voice of my pleading~*\\
as I call for help,\\
as I lift up my hands in prayer~*\\
to your holy place.

Do not drag me away with the wicked,~*\\
with the evil-doers,\\
who speak words of peace to their neighbors~*\\
but with evil in their hearts.

Blessed be the Lord for he has heard~*\\
my cry, my appeal.\\
The Lord is my strength and my shield;~*\\
in him my heart trusts.\\
I was helped, my heart rejoices~*\\
and I praise him with my song.

The Lord is the strength of his people,~*\\
a fortress where his anointed find salvation.\\
Save your people; bless Israel your heritage.~*\\
Be their shepherd and carry them for ever.

Glory to the Father, and to the Son~*\\
and to the Holy Spirit:\\
as it was in the beginning, is now,~*\\
and will be for ever. Amen.
\end{verse}

\paragraph{Ant.}{I put all my trust in the Lord, and he has not failed me.}

\subsection*{READING\hfill \normalsize 2 Corinthians 13:4}

It is true he was crucified out of weakness, but he lives by the power of God. We too are weak in him, but we live with him by God’s power in us.

\subsection*{RESPONSORY}
I am broken, crushed to the earth.\\
— Speak, Lord, your word of life.

\subsection*{CONCLUDING PRAYER}
Let us pray.

\begin{verse}
Lord Jesus Christ,\\
at noon, when darkness covered all the earth,\\
you mounted the wood of the cross\\
as the innocent victim for our redemption.\\
May your light be always with us\\
to guide us to eternal life in that kingdom\\
where you live and reign for ever and ever.\\
— Amen.
\end{verse}

\subsection*{ACCLAMATION}

Let us praise the Lord.\\
— And give him thanks.

\end{document}
