\settowidth{\versewidth}{He summons clouds from the ends of the earth; +}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 111011 101101 101}
\FirstLetter{P}raise the name \pointup{o}f the Lord,\Med\\
praise him, servants of th\pointup{e} Lord,\\
who stand in the house \pointup{o}f the Lord\Med\\
in the courts of the house of \pointup{o}ur God.

Praise the Lord for the L\pointup{o}rd is good.\Med\\
Sing a psalm to his name for he \pointup{\i}s loving.\\
For the Lord has chosen Jacob f\pointup{o}r himself\Med\\
and Israel for his own p\pointup{o}ssession.

For I know the L\pointup{o}rd is great,\Med\\
that our Lord is high above \pointup{a}ll gods.\\
The Lord does whatev\pointup{e}r he wills,\Med\\
in heaven, on earth, in th\pointup{e} seas.

He summons clouds from the ends of the \pointup{e}arth;\Flex\\
makes lightning prod\pointup{u}ce the rain;\Med\\
from his treasuries he sends forth th\pointup{e} wind.

The first-born of the Egypt\pointup{\i}ans he smote,\Med\\
of man and beast \pointup{a}like.\\
Signs and wonders he w\pointup{o}rked\Flex\\
in the midst of your l\pointup{a}nd, O Egypt,\Med\\
against Pharaoh and all h\pointup{\i}s servants.

Nations in their greatn\pointup{e}ss he struck\Med\\
and kings in their splendor h\pointup{e} slew.\\
Sihon, king of the Amor\pointup{\i}tes,\Flex\\
Og, the k\pointup{\i}ng of Bashan,\Med\\
and all the kingdoms \pointup{o}f Canaan.\\
He let Israel inher\pointup{\i}t their land;\Med\\
on his people their land he b\pointup{e}stowed.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
