\settowidth{\versewidth}{May the mountains bring forth peace for the people *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 1011 101 101 101 101 101}
\FirstLetter{O} God, give your judgment t\pointup{o} the king,\Med\\
to a king’s son y\pointup{o}ur justice,\\
that he may judge your peopl\pointup{e} in justice\Med\\
and your poor in r\pointup{\i}ght judgment.

May the mountains bring forth peace f\pointup{o}r the people\Med\\
and the h\pointup{\i}lls, justice.\\
May he defend the poor of the peopl\pointup{e}\Flex\\
and save the children \pointup{o}f the needy\Med\\
and crush the \pointup{o}ppressor.

He shall endure like the sun \pointup{a}nd the moon\Med\\
from age t\pointup{o} age.\\
He shall descend like rain \pointup{o}n the meadow,\Med\\
like raindrops on th\pointup{e} earth.

In his days just\pointup{\i}ce shall flourish\Med\\
and peace till the m\pointup{o}on fails.\\
He shall rule from s\pointup{e}a to sea,\Med\\
from the Great River to \pointup{e}arth’s bounds.

Before him his enem\pointup{\i}es shall fall,\Med\\
his foes lick th\pointup{e} dust.\\
The kings of Tarshish \pointup{a}nd the seacoasts\Med\\
shall pay h\pointup{\i}m tribute.

The kings of Sheb\pointup{a} and Seba\Med\\
shall bring h\pointup{\i}m gifts.\\
Before him all kings sh\pointup{a}ll fall prostrate,\Med\\
all nations sh\pointup{a}ll serve him.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{psalmverse}
