\settowidth{\versewidth}{from the country of Jordan and Mount Hermon, *}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 10101 101 101 101 101 101 101 101 101}
\FirstLetter{L}ike the deer th\pointup{a}t yearns\Med\\
f\pointup{o}r running streams,\\
so my soul \pointup{\i}s yearning\Med\\
f\pointup{o}r you, my God.

My soul is thirsting f\pointup{o}r God,\Med\\
the G\pointup{o}d of my life;\\
when can I enter \pointup{a}nd see\Med\\
th\pointup{e} face of God?

My tears have become m\pointup{y} bread,\Med\\
b\pointup{y} night, by day,\\
as I hear it said all the d\pointup{a}y long:\Med\\
“Wh\pointup{e}re is your God?”

These things will I r\pointup{e}member\Med\\
as I p\pointup{o}ur out my soul:\\
how I would lead the rejoic\pointup{\i}ng crowd\Med\\
int\pointup{o} the house of God,\\
amid cries of gladness and th\pointup{a}nksgiving,\Med\\
the thr\pointup{o}ng wild with joy.

Why are you cast down, m\pointup{y} soul,\Med\\
why gr\pointup{o}an within me?\\
Hope in God; I will praise h\pointup{\i}m still,\Med\\
my s\pointup{a}vior and my God.

My soul is cast down w\pointup{\i}thin me\Med\\
as \pointup{I} think of you,\\
from the country of Jordan and M\pointup{o}unt Hermon,\Med\\
from the H\pointup{i}ll of Mizar.

Deep is calling \pointup{o}n deep,\Med\\
in the roar \pointup{o}f the waters;\\
your torrents and all y\pointup{o}ur waves\Med\\
sw\pointup{e}pt over me.

By day the Lord w\pointup{\i}ll send\Med\\
his l\pointup{o}ving kindness;\\
by night I will sing t\pointup{o} him,\Med\\
praise the G\pointup{o}d of my life.

I will say to God, m\pointup{y} rock:\Med\\
“Why have y\pointup{o}u forgotten me?\\
Why do I g\pointup{o} mourning\Med\\
oppr\pointup{e}ssed by the foe?”

With cries that pierce me to m\pointup{y} heart,\Med\\
my enem\pointup{i}es revile me,\\
saying to me all the d\pointup{a}y long:\Med\\
“Wh\pointup{e}re is your God?”

Why are you cast down, m\pointup{y} soul,\Med\\
why gr\pointup{o}an within me?\\
Hope in God; I will praise h\pointup{\i}m still,\Med\\
my s\pointup{a}vior and my God.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the H\pointup{o}ly Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be for\pointup{e}ver. Amen. 
  \end{patverse}
\end{verse}
