\settowidth{\versewidth}{My hands were raised at night without ceasing; *}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{01 1101 10101 10101 10101 10101 10101 10101 1 101}
    \FirstLetter{I} cry al\pointup{o}ud to God,\Med\\
cry aloud to God that he m\pointup{a}y hear me.

In the day of my distress I sought the L\pointup{o}rd.\Flex\\
My hands were raised at night w\pointup{\i}thout ceasing;\Med\\
my soul refused to be c\pointup{o}nsoled.\\
I remembered my God \pointup{a}nd I groaned.\Med\\
I pondered and my spir\pointup{\i}t fainted.

You withheld sleep fr\pointup{o}m my eyes.\Med\\
I was troubled, I could n\pointup{o}t speak.\\
I thought of the days of l\pointup{o}ng ago\Med\\
and remembered the years l\pointup{o}ng past.\\
At night I mused with\pointup{\i}n my heart.\Med\\
I pondered and my spir\pointup{\i}t questioned.

“Will the Lord reject \pointup{u}s for ever?\Med\\
Will he show us his favor n\pointup{o} more?\\
Has his love van\pointup{\i}shed for ever?\Med\\
Has his promise come to \pointup{a}n end?\\
Does God forg\pointup{e}t his mercy\Med\\
or in anger withhold his c\pointup{o}mpassion?”

I said: “This is what caus\pointup{e}s my grief;\Med\\
that the way of the Most High h\pointup{a}s changed.”\\
I remember the deeds \pointup{o}f the Lord,\Med\\
I remember your wonders \pointup{o}f old,\\
I muse on \pointup{a}ll your works\Med\\
and ponder your might\pointup{y} deeds.

Your ways, O G\pointup{o}d, are holy.\Med\\
What god is as great as \pointup{o}ur God?\\
You are the God wh\pointup{o} works wonders.\Med\\
You showed your power among th\pointup{e} peoples.\\
Your strong arm red\pointup{e}emed your people,\Med\\
the sons of Jacob \pointup{a}nd Joseph.

The waters saw y\pointup{o}u, O God,\Med\\
the waters saw you \pointup{a}nd trembled;\\
the depths were m\pointup{o}ved with terror.\Med\\
The clouds poured d\pointup{o}wn rain,\\
the skies sent f\pointup{o}rth their voice;\Med\\
your arrows flashed to \pointup{a}nd fro.

Your thunder rolled r\pointup{o}und the sky,\Med\\
your flashes lighted up th\pointup{e} world.\\
The earth was m\pointup{o}ved and trembled\Med\\
when your way led through th\pointup{e} sea,\\
your path through the m\pointup{\i}ghty waters\Med\\
and no one saw y\pointup{o}ur footprints.

You guided your people l\pointup{\i}ke a flock\Med\\
by the hand of Moses \pointup{a}nd Aaron.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
