\begin{psalmverse}
  \begin{patverse}
    \indentpattern{0101 1011 101 1 101 11011 101 1 101}
    \FirstLetter{H}ave mercy on me, God, h\pointup{a}ve mercy\Med\\
for in you my soul has tak\pointup{e}n refuge.\\
In the shadow of your wings I t\pointup{a}ke refuge\Med\\
till the storms of destruction p\pointup{a}ss by.

I call to you God the M\pointup{o}st High,\Med\\
to you who have always been m\pointup{y} help.\\
May you send from heaven and save m\pointup{e}\Flex\\
and shame those who \pointup{a}ssail me.\Med\\
May God send his truth and h\pointup{\i}s love.

My soul lies down am\pointup{o}ng lions,\Med\\
who would devour the sons \pointup{o}f men.\\
Their teeth are spears \pointup{a}nd arrows,\Med\\
their tongue a sharp\pointup{e}ned sword.

O God, arise above th\pointup{e} heavens;\Med\\
may your glory shine \pointup{o}n earth!

They laid a snare for m\pointup{y} steps\Med\\
my soul was b\pointup{o}wed down.\\
They dug a pit in m\pointup{y} path\Med\\
but fell in it th\pointup{e}mselves.

My heart is ready, O G\pointup{o}d,\Flex\\
my heart \pointup{\i}s ready.\Med\\
I will sing, I will sing y\pointup{o}ur praise.\\
Awake, my s\pointup{o}ul;\Flex\\
awake, lyre \pointup{a}nd harp,\Med\\
I will awake th\pointup{e} dawn.

I will thank you, Lord, among th\pointup{e} peoples,\Med\\
among the nations I w\pointup{\i}ll praise you\\
for your love reaches to th\pointup{e} heavens\Med\\
and your truth to th\pointup{e} skies.

O God, arise above th\pointup{e} heavens;\Med\\
may your glory shine \pointup{o}n earth.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
