\settowidth{\versewidth}{He is throned on the cherubim; the earth quakes. *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{011 11 11 11 11 11 11 11 101}
\FirstLetter{T}he Lord is king; the peoples trembl\pointup{e}.\Flex\\
He is throned on the cherubim; the \pointup{e}arth quakes.\Med\\
The Lord is gr\pointup{e}at in Zion.

He is supreme over all the peopl\pointup{e}s.\Flex\\
Let them praise his name, so terrible \pointup{a}nd great,\Med\\
he is holy, f\pointup{u}ll of power.

You are a king who loves what is r\pointup{\i}ght;\Flex\\
you have established equity, justice \pointup{a}nd right;\Med\\
you have established th\pointup{e}m in Jacob.

Exalt the Lord our G\pointup{o}d;\Flex\\
bow down before Zion, h\pointup{\i}s footstool.\Med\\
He the L\pointup{o}rd is holy.

Among his priests were Aaron and Mos\pointup{e}s,\Flex\\
among those who invoked his name w\pointup{a}s Samuel.\Med\\
They invoked the Lord \pointup{a}nd he answered.

To them he spoke in the pillar of cl\pointup{o}ud.\Flex\\
They did his will; they kept th\pointup{e} law,\Med\\
which he, the L\pointup{o}rd, had given.

O Lord our God, you answered th\pointup{e}m.\Flex\\
For them you were a God who f\pointup{o}rgives;\Med\\
yet you punished th\pointup{e}ir offenses.

Exalt the Lord our G\pointup{o}d;\Flex\\
bow down before his hol\pointup{y} mountain\Med\\
for the Lord our G\pointup{o}d is holy.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the H\pointup{o}ly Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forev\pointup{e}r. Amen.
  \end{patverse}
\end{verse}
