\begin{verse}
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 101 101 101 101 101 101}
\FirstLetter{H}ave mercy on me, God, \pointup{\i}n your kindness.\Med\\
In your compassion blot out my \pointup{o}ffense.\\
O wash me more and more fr\pointup{o}m my guilt\Med\\
and cleanse me from m\pointup{y} sin.

My offenses trul\pointup{y} I know them;\Med\\
my sin is always b\pointup{e}fore me\\
Against you, you alone, h\pointup{a}ve I sinned;\Med\\
what is evil in your sight I h\pointup{a}ve done.

That you may be justified when y\pointup{o}u give sentence\Med\\
and be without reproach when y\pointup{o}u judge.\\
O see, in guilt \pointup{\i} was born,\Med\\
a sinner was I c\pointup{o}nceived.

Indeed you love truth \pointup{\i}n the heart;\Med\\
then in the secret of my heart teach m\pointup{e} wisdom.\\
O purify me, then I sh\pointup{a}ll be clean;\Med\\
O wash me, I shall be whiter th\pointup{a}n snow.

Make me hear rejoic\pointup{\i}ng and gladness,\Med\\
that the bones you have crushed may r\pointup{e}vive.\\
From my sins turn aw\pointup{a}y your face\Med\\
and blot out all m\pointup{y} guilt.

A pure heart create for m\pointup{e}, O God,\Med\\
put a steadfast spirit w\pointup{\i}thin me.\\
Do not cast me away fr\pointup{o}m your presence,\Med\\
nor deprive me of your hol\pointup{y} spirit.

Give me again the joy \pointup{o}f your help;\Med\\
with a spirit of fervor s\pointup{u}stain me,\\
that I may teach transgress\pointup{o}rs your ways\Med\\
and sinners may return t\pointup{o} you.

O rescue me, G\pointup{o}d, my helper,\Med\\
and my tongue shall ring out y\pointup{o}ur goodness.\\
O Lord, op\pointup{e}n my lips\Med\\
and my mouth shall declare y\pointup{o}ur praise.

For in sacrifice you take n\pointup{o} delight,\Med\\
burnt offering from me you would r\pointup{e}fuse,\\
my sacrifice, a c\pointup{o}ntrite spirit,\Med\\
a humbled, contrite heart you will n\pointup{o}t spurn.

In your goodness, show fav\pointup{o}r to Zion:\Med\\
rebuild the walls of J\pointup{e}rusalem.\\
Then you will be pleased with l\pointup{a}wful sacrifice,\Med\\
holocausts offered on y\pointup{o}ur altar.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
  \end{verse}
