\settowidth{\versewidth}{That you may be justified when you give sentence *}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 101 101 101 101 101 101}
    \FirstLetter{H}ave mercy on me, God, in your k\pointup{\i}ndness.\Med\\
In your compassion blot out my \pointup{o}ffense.\\
O wash me more and more from m\pointup{y} guilt\Med\\
and cleanse me from m\pointup{y} sin.

My offenses truly \pointup{I} know them;\Med\\
my sin is always b\pointup{e}fore me\\
Against you, you alone, have \pointup{I} sinned;\Med\\
what is evil in your sight I h\pointup{a}ve done.

That you may be justified when you g\pointup{\i}ve sentence\Med\\
and be without reproach when y\pointup{o}u judge.\\
O see, in guilt I w\pointup{a}s born,\Med\\
a sinner was I c\pointup{o}nceived.

Indeed you love truth in th\pointup{e} heart;\Med\\
then in the secret of my heart teach m\pointup{e} wisdom.\\
O purify me, then I shall b\pointup{e} clean;\Med\\
O wash me, I shall be whiter th\pointup{a}n snow.

Make me hear rejoicing \pointup{a}nd gladness,\Med\\
that the bones you have crushed may r\pointup{e}vive.\\
From my sins turn away y\pointup{o}ur face\Med\\
and blot out all m\pointup{y} guilt.

A pure heart create for me, \pointup{O} God,\Med\\
put a steadfast spirit w\pointup{\i}thin me.\\
Do not cast me away from y\pointup{o}ur presence,\Med\\
nor deprive me of your hol\pointup{y} spirit.

Give me again the joy of y\pointup{o}ur help;\Med\\
with a spirit of fervor s\pointup{u}stain me,\\
that I may teach transgressors y\pointup{o}ur ways\Med\\
and sinners may return t\pointup{o} you.

O rescue me, God, m\pointup{y} helper,\Med\\
and my tongue shall ring out y\pointup{o}ur goodness.\\
O Lord, open m\pointup{y} lips\Med\\
and my mouth shall declare y\pointup{o}ur praise.

For in sacrifice you take no d\pointup{e}light,\Med\\
burnt offering from me you would r\pointup{e}fuse,\\
my sacrifice, a contr\pointup{\i}te spirit,\Med\\
a humbled, contrite heart you will n\pointup{o}t spurn.

In your goodness, show favor t\pointup{o} Zion:\Med\\
rebuild the walls of J\pointup{e}rusalem.\\
Then you will be pleased with lawf\pointup{u}l sacrifice,\Med\\
holocausts offered on y\pointup{o}ur altar.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
