\settowidth{\versewidth}{so I left them in their stubbornness of heart *}
\begin{verse}%%[\versewidth]%
  \begin{patverse}
    \indentpattern{01 101 101 101 101 1011 101 101 101 101}
\FirstLetter{R}ing out your joy to G\pointup{o}d our strength,\Med\\
shout in triumph to the God \pointup{o}f Jacob.

Raise a song and s\pointup{o}und the timbrel,\Med\\
the sweet-sounding harp and th\pointup{e} lute;\\
blow the trumpet \pointup{a}t the new moon,\Med\\
when the moon is full, on \pointup{o}ur feast.

For this is Isr\pointup{a}el’s law,\Med\\
a command of the God \pointup{o}f Jacob.\\
He imposed it as a r\pointup{u}le on Joseph,\Med\\
when he went out against the land \pointup{o}f Egypt.

A voice I did not know s\pointup{a}id to me:\Med\\
“I freed your shoulder from th\pointup{e} burden;\\
your hands were freed fr\pointup{o}m the load.\Med\\
You called in distress and \pointup{I} saved you.

I answered, concealed \pointup{\i}n the storm cloud;\Med\\
at the waters of Meribah I test\pointup{e}d you.\\
Listen, my people, t\pointup{o} my warning.\Med\\
O Israel, if only you w\pointup{o}uld heed!

Let there be no foreign g\pointup{o}d among you.\Med\\
no worship of an ali\pointup{e}n god.\\
I am the Lord your G\pointup{o}d,\Flex\\
who brought you from the l\pointup{a}nd of Egypt.\Med\\
Open wide your mouth and I w\pointup{\i}ll fill it.

But my people did not h\pointup{e}ed my voice\Med\\
and Israel would not \pointup{o}bey,\\
so I left them in their stubbornn\pointup{e}ss of heart\Med\\
to follow their own d\pointup{e}signs.

O that my peopl\pointup{e} would heed me,\Med\\
that Israel would walk in m\pointup{y} ways!\\
At once I would subd\pointup{u}e their foes,\Med\\
turn my hand against th\pointup{e}ir enemies.

The Lord’s enemies would cringe \pointup{a}t their feet\Med\\
and their subjection would last f\pointup{o}r ever.\\
But Israel I would feed with f\pointup{\i}nest wheat\Med\\
and fill them with honey from th\pointup{e} rock.”

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
