\settowidth{\versewidth}{I will praise you, Lord my God, with all my heart *}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 11 101 11 101 1001 101 }
\FirstLetter{T}urn your ear, O Lord, \pointup{a}nd give answer\Med\\
for I am poor \pointup{a}nd needy.\\
Preserve my life, for \pointup{I} am faithful;\Med\\
save the servant who trusts \pointup{\i}n you.

You are my God, have mercy \pointup{o}n me, Lord,\Med\\
for I cry to you all the d\pointup{a}y long.\\
Give joy to your serv\pointup{a}nt, O Lord,\Med\\
for to you I lift up m\pointup{y} soul.

O Lord, you are good \pointup{a}nd forgiving,\Med\\
full of love to all wh\pointup{o} call.\\
Give heed, O Lord, t\pointup{o} my prayer\Med\\
and attend to the sound of m\pointup{y} voice.

In the day of distress \pointup{I} will call\Med\\
and surely you will r\pointup{e}ply.\\
Among the gods there is none like y\pointup{o}u, O Lord;\Med\\
nor work to compare w\pointup{\i}th yours.

All the nations shall come t\pointup{o} adore you\Med\\
and glorify your name, \pointup{O} Lord:\\
for you are great and do marv\pointup{e}lous deeds,\Med\\
you who alone \pointup{a}re God.

Show me, Lord, your w\pointup{a}y\Flex\\
so that I may walk \pointup{i}n your truth.\Med\\
Guide my heart to fear y\pointup{o}ur name.

I will praise you, Lord my God, with \pointup{a}ll my heart\Med\\
and glorify your name f\pointup{o}r ever;\\
for your love to me h\pointup{a}s been great:\Med\\
you have saved me from the depths of th\pointup{e} grave.

The proud have risen against m\pointup{e};\Flex\\
ruthless men s\pointup{e}ek my life;\Med\\
to you they pay n\pointup{o} heed.

But you, God of mercy \pointup{a}nd compassion,\Med\\
slow to anger, \pointup{O} Lord,\\
abounding in l\pointup{o}ve and truth,\Med\\
turn and take pity \pointup{o}n me.

O give your strength t\pointup{o} your servant\Med\\
and save your handm\pointup{a}id’s son.\\
Show me the sign of your fav\pointup{o}r\Flex\\
that my foes may see t\pointup{o} their shame\Med\\
that you console me and give me y\pointup{o}ur help.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{i}ng, is now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
