\settowidth{\versewidth}{And you brought them in and planted them on the mountain of your inheritance— *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01 101 1011 1011 101 1 101 101}
    \FirstLetter{I} will sing to the Lord, for he is gloriously tr\pointup{\i}umphant;\Med\\
horse and chariot he has cast into th\pointup{e} sea.

My strength and my courage is th\pointup{e} Lord,\Med\\
and he has been m\pointup{y} savior.\\
He is my God, \pointup{I} praise him;\Med\\
the God of my father, I \pointup{e}xtol him.

The Lord is a warrior, Lord is h\pointup{\i}s name!\Med\\
Pharaoh’s chariots and army he hurled into th\pointup{e} sea.\\
At a breath of your anger the waters piled \pointup{u}p,\Flex\\
the flowing waters stood like \pointup{a} mound,\Med\\
the flood waters congealed in the midst of th\pointup{e} sea.

The enemy boasted, “I will pursue and overtake th\pointup{e}m;\Flex\\
I will divide the spoils and have my fill \pointup{o}f them;\Med\\
I will draw my sword; my hand shall d\pointup{e}spoil them!”\\
When your wind blew, the sea cov\pointup{e}red them;\Med\\
like lead they sank in the might\pointup{y} waters.

Who is like to you among the gods, \pointup{O} Lord?\Med\\
Who is like to you, magnificent \pointup{\i}n holiness?\\
O terrible in renown, worker \pointup{o}f wonders,\Med\\
when you stretched out your right hand, the earth swall\pointup{o}wed them!

In your mercy you led the people you r\pointup{e}deemed;\Med\\
in your strength you guided them to your hol\pointup{y} dwelling.

And you brought them in and planted them on the mountain of your \pointup{\i}nheritance—\Med\\
the place where you made your seat, \pointup{O} Lord,\\
the sanctuary, O Lord, which your hands \pointup{e}stablished.\Med\\
The Lord shall reign forever \pointup{a}nd ever.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
