\settowidth{\versewidth}{He will guard the footsteps of his faithful ones, *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01 101 101 10101 1101 101 10101 101 101}
    \FirstLetter{M}y heart exults \pointup{\i}n the Lord,\Med\\
my horn is exalted in m\pointup{y} God.

I have swallowed \pointup{u}p my enemies;\Med\\
I rejoice in m\pointup{y} victory.\\
There is no Holy One l\pointup{\i}ke the Lord;\Med\\
there is no Rock like \pointup{o}ur God.

Speak boastfull\pointup{y} no longer,\Med\\
nor let arrogance issue from y\pointup{o}ur mouths.\\
For an all-knowing God \pointup{\i}s the Lord,\Med\\
a God who judg\pointup{e}s deeds.

The bows of the might\pointup{y} are broken,\Med\\
while the tottering gird \pointup{o}n strength.\\
The well-fed hire themselves \pointup{o}ut for bread,\Med\\
while the hungry batten \pointup{o}n spoil.\\
The barren wife bears s\pointup{e}ven sons,\Med\\
while the mother of man\pointup{y} languishes.

The Lord puts to death and gives l\pointup{\i}fe;\Flex\\
he casts down to the n\pointup{e}ther world;\Med\\
he raises up \pointup{a}gain.\\
The Lord makes poor \pointup{a}nd makes rich,\Med\\
he humbles, he also \pointup{e}xalts.

He raises the needy fr\pointup{o}m the dust;\Med\\
from the ash heap he lifts up th\pointup{e} poor,\\
to seat th\pointup{e}m with nobles\Med\\
and make a glorious throne th\pointup{e}ir heritage.

For the pillars of the earth \pointup{a}re the Lord’s,\Med\\
and he has set the world \pointup{u}pon them.\\
He will guard the footsteps \pointup{o}f his faithful ones,\Med\\
but the wicked shall perish in th\pointup{e} darkness.\\
For not by strength does m\pointup{a}n prevail;\Med\\
the Lord’s foes shall b\pointup{e} shattered.

The Most High in h\pointup{e}aven thunders;\Med\\
the Lord judges the ends of th\pointup{e} earth.\\
Now may he give strength t\pointup{o} his king\Med\\
and exalt the horn of his \pointup{a}nointed!

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{psalmverse}
