\settowidth{\versewidth}{for night and day your hand was heavy upon me.}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{01011 1101 10101 101011 101 11011 101 101}
\FirstLetter{H}appy the man whose offense \pointup{\i}s forgiven,\Med\\
whose sin is r\pointup{e}mitted.\\
O happy the man to whom the L\pointup{o}rd\Flex\\
imp\pointup{u}tes no guilt,\Med\\
in whose spirit is n\pointup{o} guile.

I kept it secret and my frame was wast\pointup{e}d.\Flex\\
I groaned \pointup{a}ll day long,\Med\\
for night and day your hand was heavy \pointup{u}pon me.\\
Indeed my strength w\pointup{a}s dried up\Med\\
as by the summ\pointup{e}r’s heat.

But now I have acknowl\pointup{e}dged my sins;\Med\\
my guilt I did n\pointup{o}t hide.\\
I said: “I w\pointup{\i}ll confess\Med\\
my offense to th\pointup{e} Lord.”\\
And you, Lord, h\pointup{a}ve forgiven\Med\\
the guilt of m\pointup{y} sin.

So let every good man pr\pointup{a}y to you\Med\\
in the time \pointup{o}f need.\\
The floods of water m\pointup{a}y reach high\Med\\
but him they shall n\pointup{o}t reach.\\
You are my hiding place, O L\pointup{o}rd;\Flex\\
you save me fr\pointup{o}m distress.\Med\\
You surround me with cries of d\pointup{e}liverance.

I will instruct y\pointup{o}u and teach you\Med\\
the way you sh\pointup{o}uld go;\\
I will g\pointup{\i}ve you counsel\Med\\
with my eye \pointup{u}pon you.

Be not like horse and mule, unintell\pointup{\i}gent,\Flex\\
needing bridl\pointup{e} and bit;\Med\\
else they will not \pointup{a}pproach you.\Med\\
Many sorrows has the wick\pointup{e}d\\
but he who trusts \pointup{\i}n the Lord,\Med\\
loving mercy s\pointup{u}rrounds him.

Rejoice, rejoice \pointup{\i}n the Lord,\Med\\
exult, y\pointup{o}u just!\\
O come, ring \pointup{o}ut your joy,\Med\\
all you upright \pointup{o}f heart.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
