\settowidth{\versewidth}{no place to offer first fruits, to find favor with you.}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{011 11 11 1 11 11 11 11 101011 1 101}
\FirstLetter{B}lessed are you, and praisew\pointup{o}rthy,\Flex\\
O Lord, the God \pointup{o}f our fathers,\Med\\
and glorious forever is y\pointup{o}ur name.

For you are just in all you have d\pointup{o}ne;\Flex\\
all your deeds are faultless, all y\pointup{o}ur ways right,\Med\\
and all your judgm\pointup{e}nts proper.

For we have sinned and transgr\pointup{e}ssed\Flex\\
by depart\pointup{\i}ng from you,\Med\\
and we have done every kind \pointup{o}f evil.

For your name’s sake, do not deliver us \pointup{u}p forever,\Med\\
or make void y\pointup{o}ur covenant.

Do not take away your mercy from \pointup{u}s,\Flex\\
for the sake of Abraham, y\pointup{o}ur beloved,\Med\\
Isaac your servant, and Israel your hol\pointup{y} one,

To whom you promised to multiply their offspr\pointup{\i}ng\Flex\\
like the st\pointup{a}rs of heaven,\Med\\
or the sand on the shore of th\pointup{e} sea.

For we are reduced, O Lord, beyond any other nat\pointup{\i}on,\Flex\\
brought low everywhere in the w\pointup{o}rld this day\Med\\
because of \pointup{o}ur sins.

We have in our day no prince, prophet, or lead\pointup{e}r,\Flex\\
no holocaust, sacrifice, oblat\pointup{\i}on, or incense,\Med\\
no place to offer first fruits, to find favor w\pointup{\i}th you.

But with contrite heart and h\pointup{u}mble spirit\Med\\
let us be r\pointup{e}ceived;\\
as though it were holocausts of r\pointup{a}ms and bullocks,\Med\\
or thousands of f\pointup{a}t lambs,\\
so let our sacrifice be in your presence tod\pointup{a}y\Flex\\
as we follow you \pointup{u}nreservedly;\Med\\
for those who trust in you cannot be put t\pointup{o} shame.

And now we follow you with \pointup{o}ur whole heart,\Med\\
we fear you and we pray t\pointup{o} you.

Glory to the Father and t\pointup{o} the Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
    and will be for ever. \pointupl{A}men.
  \end{patverse}
\end{verse}
