\settowidth{\versewidth}{let your face shine on us and we shall be saved.}
\begin{verse}%%[\versewidth]%
  \begin{patverse}
    \indentpattern{010101 1 10101 1 101 101 101 10101 101 1 101}
\FirstLetter{O} shepherd of Isr\pointup{a}el, hear us,\Med\\
you who lead Jos\pointup{e}ph’s flock,\\
shine forth from your cherub\pointup{\i}m throne\Med\\
upon Ephraim, Benjamin, M\pointup{a}nasseh.\\
O Lord, rouse up y\pointup{o}ur might,\Med\\
O Lord, come to \pointup{o}ur help.

God of hosts bring \pointup{u}s back;\Med\\
let your face shine on us and we shall b\pointup{e} saved.

Lord God of hosts, h\pointup{o}w long\Med\\
will you frown on your peopl\pointup{e}’s plea?\\
You have fed them with tears for th\pointup{e}ir bread,\Med\\
an abundance of tears for th\pointup{e}ir drink.\\
You have made us the taunt of \pointup{o}ur neighbors,\Med\\
our enemies laugh us t\pointup{o} scorn.

God of hosts, bring \pointup{u}s back;\Med\\
let your face shine on us and we shall b\pointup{e} saved.

You brought a vine out \pointup{o}f Egypt;\Med\\
to plant it you drove out th\pointup{e} nations.\\
Before it you cleared th\pointup{e} ground;\Med\\
it took root and spread through th\pointup{e} land.

The mountains were covered with \pointup{\i}ts shadow,\Med\\
the cedars of God with \pointup{\i}ts boughs.\\
It stretched out its branches to th\pointup{e} sea,\Med\\
to the Great River it stretched out \pointup{\i}ts shoots.

Then why have you broken down \pointup{\i}ts walls?\Med\\
It is plucked by all who p\pointup{a}ss by.\\
It is ravaged by the boar of th\pointup{e} forest,\Med\\
devoured by the beasts of th\pointup{e} field.

God of hosts, turn again, we \pointup{\i}mplore,\Med\\
look down from heaven \pointup{a}nd see.\\
Visit the vine and pr\pointup{o}tect it,\Med\\
the vine your right hand h\pointup{a}s planted.\\
Men have burnt it with fire and d\pointup{e}stroyed it.\Med\\
May they perish at the frown of y\pointup{o}ur face.

May your hand be on the man you h\pointup{a}ve chosen,\Med\\
the man you have given y\pointup{o}ur strength.\\
And we shall never forsake you \pointup{a}gain;\Med\\
give us life that we may call upon y\pointup{o}ur name.

God of hosts, bring \pointup{u}s back;\Med\\
let your face shine on us and we shall b\pointup{e} saved.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
