\begin{verse}
  \begin{patverse}
    \indentpattern{01011 10101 1011 101 101 10101 1 101}
    \FirstLetter{L}ord, listen to m\pointup{y} prayer:\Med\\
    turn your ear to my \pointup{a}ppeal.\\
    You are faithful, you are just; give answ\pointup{e}r.\Flex\\
    Do not call your servant t\pointup{o} judgement\Med\\
    for no one is just in y\pointup{o}ur sight.

    The enemy pursues m\pointup{y} soul;\Med\\
    he has crushed my life to th\pointup{e} ground;\\
    he has made me dwell \pointup{\i}n darkness\Med\\
    like the dead, long f\pointup{o}rgotten.\\
    Therefore my spir\pointup{\i}t fails;\Med\\
    my heart is numb w\pointup{\i}thin me.

    I remember the days that \pointup{a}re past:\Med\\
    I ponder all y\pointup{o}ur works.\\
    I muse on what your hand has wr\pointup{o}ught\Flex\\
    and to you I stretch out m\pointup{y} hands.\Med\\
    Like a parched land my soul thirsts f\pointup{o}r you.

    Lord, make haste \pointup{a}nd answer;\Med\\
    for my spirit fails w\pointup{\i}thin me.\\
    Do not hide y\pointup{o}ur face\Med\\
    lest I become like those in th\pointup{e} grave.

    In the morning let me know y\pointup{o}ur love\Med\\
    for I put my trust \pointup{\i}n you.\\
    Make me know the way I sh\pointup{o}uld walk:\Med\\
    to you I lift up m\pointup{y} soul.

    Rescue me, Lord, from m\pointup{y} enemies;\Med\\
    I have fled to you f\pointup{o}r refuge.\\
    Teach me to do y\pointup{o}ur will\Med\\
    for you, O Lord, are m\pointup{y} God.\\
    Let your good spir\pointup{\i}t guide me\Med\\
    in ways that are level \pointup{a}nd smooth.

    For your name’s sake, Lord, save m\pointup{y} life;\Med\\
    in your justice save my soul from d\pointup{\i}stress.

    Glory to the Father and to th\pointup{e} Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
    as it was in the beginning, \pointup{\i}s now,\Med\\
    and will be for ever. \pointupl{A}men.
  \end{patverse}
  \end{verse}
