\settowidth{\versewidth}{I shall not die, I shall live and recount his deeds.}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01 10101 10101 101 101011 10101 10101 10101 10101 10101 10101 101}
    \FirstLetter{G}ive thanks to the Lord for h\pointup{e} is good,\Med\\
    for his love endures f\pointup{o}r ever.

    Let the sons of Isr\pointup{a}el say:\Med\\
    “His love endures f\pointup{o}r ever.”\\
    Let the sons of \pointupl{A}aron say:\Med\\
    “His love endures f\pointup{o}r ever.”\\
    Let those who fear th\pointup{e} Lord say:\Med\\
    “His love endures f\pointup{o}r ever.”

    I called to the Lord in m\pointup{y} distress;\Med\\
    he answered \pointup{a}nd freed me.\\
    The Lord is at my side; I d\pointup{o} not fear.\Med\\
    what can man do \pointup{a}gainst me?\\
    The Lord is at my side \pointup{a}s my helper;\Med\\
    I shall look down on m\pointup{y} foes.

    It is better to take refuge \pointup{\i}n the Lord\Med\\
    than to trust \pointup{\i}n men;\\
    it is better to take refuge \pointup{\i}n the Lord\Med\\
    than to trust \pointup{\i}n princes.

    The nations \pointup{a}ll encompassed me;\Med\\
    in the Lord’s name \pointup{I} crushed them.\\
    They compassed me, compassed m\pointup{e} about;\Med\\
    in the Lord’s name \pointup{I} crushed them.\\
    They compassed me about like b\pointup{e}es;\Flex\\
    they blazed like a fire \pointup{a}mong thorns.\Med\\
    In the Lord’s name \pointup{I} crushed them.

    I was hard-pressed \pointup{a}nd was falling\Med\\
    but the Lord came t\pointup{o} help me.\\
    The Lord is my strength \pointup{a}nd my song;\Med\\
    he is m\pointup{y} savior.\\
    There are shouts of j\pointup{o}y and victory\Med\\
    in the tents of th\pointup{e} just.

    The Lord’s right h\pointup{a}nd has triumphed;\Med\\
    his right h\pointup{a}nd raised me.\\
    The Lord’s right h\pointup{a}nd has triumphed;\Med\\
    I shall not die, I shall live and recount h\pointup{\i}s deeds.\\
    I was punished, I was punished b\pointup{y} the Lord,\Med\\
    but not doomed t\pointup{o} die.

    Open to me the g\pointup{a}tes of holiness:\Med\\
    I will enter and g\pointup{\i}ve thanks.\\
    This is the L\pointup{o}rd’s own gate\Med\\
    where the just m\pointup{a}y enter.\\
    I will thank you for y\pointup{o}u have answered\Med\\
    and you are m\pointup{y} savior.

    The stone which the build\pointup{e}rs rejected\Med\\
    has become the corn\pointup{e}r stone.\\
    This is the work \pointup{o}f the Lord,\Med\\
    a marvel in \pointup{o}ur eyes.\\
    This day was made b\pointup{y} the Lord;\Med\\
    we rejoice and \pointup{a}re glad.

    O Lord, grant \pointup{u}s salvation;\Med\\
    O Lord, grant s\pointup{u}ccess.\\
    Blessed in the name \pointup{o}f the Lord\Med\\
    is he wh\pointup{o} comes.\\
    We bless you from the house \pointup{o}f the Lord;\Med\\
    the Lord God is \pointup{o}ur light.

    Go forward in process\pointup{\i}on with branches\Med\\
    even to th\pointup{e} altar.\\
    You are my G\pointup{o}d, I thank you.\Med\\
    My God, \pointup{I} praise you.\\
    Give thanks to the Lord for h\pointup{e} is good;\Med\\
    for his love endures f\pointup{o}r ever.

    Glory to the Father and t\pointup{o} the Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
    as it was in the beginn\pointup{\i}ng, is now,\Med\\
    and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
