\begin{verse}
  \begin{patverse}
    \indentpattern{011 11 11 11 11 11 11 101 101 101}
\FirstLetter{O} sing a new song to the L\pointup{o}rd,\Flex\\
sing to the Lord all th\pointup{e} earth.\Med\\
O sing to the Lord, bless h\pointup{\i}s name.

Proclaim his help day by d\pointup{a}y,\Flex\\
tell among the nations h\pointup{\i}s glory\Med\\
and his wonders among all th\pointup{e} peoples.

The Lord is great and worthy of pr\pointup{a}ise,\Flex\\
to be feared above \pointup{a}ll gods;\Med\\
the gods of the heathens \pointup{a}re naught.

It was the Lord who made the heav\pointup{e}ns,\Flex\\
his are majesty and state \pointup{a}nd power\Med\\
and splendor in his hol\pointup{y} place.

Give the Lord, you families of peopl\pointup{e}s,\Flex\\
give the Lord glory \pointup{a}nd power;\Med\\
give the Lord the glory of h\pointup{\i}s name.

Bring an offering and enter his c\pointup{o}urts,\Flex\\
worship the Lord in h\pointup{\i}s temple.\Med\\
O earth, tremble b\pointup{e}fore him.

Proclaim to the nations: God is k\pointup{\i}ng.\Flex\\
The world he made firm in \pointup{\i}ts place;\Med\\
he will judge the people \pointup{\i}n fairness.

Let the heavens rejoice and earth b\pointup{e} glad,\Med\\
let the sea and all within it thund\pointup{e}r praise,\\
let the land and all it bears r\pointup{e}joice,\Med\\
all the trees of the wood shout f\pointup{o}r joy

at the presence of the Lord for h\pointup{e} comes,\Med\\
he comes to rule th\pointup{e} earth.\\
With justice he will rule th\pointup{e} world,\Med\\
he will judge the peoples with h\pointup{\i}s truth.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
