\begin{psalmverse}
  \begin{patverse}
    \indentpattern{01 1101 10101 10101 10101 10101 10101 10101 1 101}
    \FirstLetter{I} cry aloud t\pointup{o} God,\Med\\
cry aloud to God that he m\pointup{a}y hear me.

In the day of my distress I sought the L\pointup{o}rd.\Flex\\
My hands were raised at night with\pointup{o}ut ceasing;\Med\\
my soul refused to be c\pointup{o}nsoled.\\
I remembered my God and \pointup{I} groaned.\Med\\
I pondered and my spir\pointup{\i}t fainted.

You withheld sleep from m\pointup{y} eyes.\Med\\
I was troubled, I could n\pointup{o}t speak.\\
I thought of the days of long \pointup{a}go\Med\\
and remembered the years l\pointup{o}ng past.\\
At night I mused within m\pointup{y} heart.\Med\\
I pondered and my spir\pointup{\i}t questioned.

“Will the Lord reject us f\pointup{o}r ever?\Med\\
Will he show us his favor n\pointup{o} more?\\
Has his love vanished f\pointup{o}r ever?\Med\\
Has his promise come to \pointup{a}n end?\\
Does God forget h\pointup{\i}s mercy\Med\\
or in anger withhold his c\pointup{o}mpassion?”

I said: “This is what causes m\pointup{y} grief;\Med\\
that the way of the Most High h\pointup{a}s changed.”\\
I remember the deeds of th\pointup{e} Lord,\Med\\
I remember your wonders \pointup{o}f old,\\
I muse on all y\pointup{o}ur works\Med\\
and ponder your might\pointup{y} deeds.

Your ways, O God, \pointup{a}re holy.\Med\\
What god is as great as \pointup{o}ur God?\\
You are the God who w\pointup{o}rks wonders.\Med\\
You showed your power among th\pointup{e} peoples.\\
Your strong arm redeemed y\pointup{o}ur people,\Med\\
the sons of Jacob \pointup{a}nd Joseph.

The waters saw you, \pointup{O} God,\Med\\
the waters saw you \pointup{a}nd trembled;\\
the depths were moved w\pointup{\i}th terror.\Med\\
The clouds poured d\pointup{o}wn rain,\\
the skies sent forth th\pointup{e}ir voice;\Med\\
your arrows flashed to \pointup{a}nd fro.

Your thunder rolled round th\pointup{e} sky,\Med\\
your flashes lighted up th\pointup{e} world.\\
The earth was moved \pointup{a}nd trembled\Med\\
when your way led through th\pointup{e} sea,\\
your path through the might\pointup{y} waters\Med\\
and no one saw y\pointup{o}ur footprints.

You guided your people like \pointup{a} flock\Med\\
by the hand of Moses \pointup{a}nd Aaron.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{psalmverse}
