%% \settowidth{\versewidth}{Their princes were thrown down by the side of the rock; *}
\begin{verse}[\versewidth]
\begin{patverse}
\indentpattern{0101 101 101 101 101 101}
\FirstLetter{I} have called to you, Lord; hast\pointup{e}n to help me!\Med\\
    Hear my voice when I cry t\pointup{o} you.\\
Let my prayer arise before y\pointup{o}u like incense,\Med\\
    the raising of my hands like an evening \pointup{o}blation.

Set, O Lord, a guard ov\pointup{e}r my mouth;\Med\\
    keep watch, O Lord, at the door of m\pointup{y} lips!\\
Do not turn my heart to things th\pointup{a}t are wrong,\Med\\
    to evil deeds with men who \pointup{a}re sinners.

Never allow me to share \pointup{\i}n their feasting.\Med\\
    If a good man strikes or reproves me it \pointup{\i}s kindness;\\
but let the oil of the wicked not an\pointup{o}int my head.\Med\\
    Let my prayer be ever against th\pointup{e}ir malice.

Their princes were thrown down by the side \pointup{o}f the rock;\Med\\
    then they understood that my words w\pointup{e}re kind.\\
As a millstone is shattered to pieces \pointup{o}n the ground,\Med\\
    so their bones were strewn at the mouth of th\pointup{e} grave.

To you, Lord God, my \pointup{e}yes are turned:\Med\\
    in you I take refuge; spare m\pointup{y} soul!\\
From the trap they have laid for me k\pointup{e}ep me safe:\Med\\
    keep me from the snares of those who d\pointup{o} evil.

Glory to the Father and t\pointup{o} the Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be for ever. \pointupl{A}men.
\end{patverse}
\end{verse}
