\settowidth{\versewidth}{for the work of your hands I shout with joy.}
\begin{psalmverse}%%[\versewidth]%
  \begin{patverse}
    \indentpattern{010101 10101 10101 10101 10101 101}
\FirstLetter{I}t is good to give thanks t\pointup{o} the Lord,\Med\\
    to make music to your name, O M\pointup{o}st High,\\
to proclaim your love \pointup{\i}n the morning\Med\\
    and your truth in the watches of th\pointup{e} night,\\
on the ten-stringed lyre \pointup{a}nd the lute,\Med\\
    with the murmuring sound of th\pointup{e} harp.

Your deeds, O Lord, have m\pointup{a}de me glad;\Med\\
    for the work of your hands I shout w\pointup{\i}th joy.\\
O Lord, how great \pointup{a}re your works!\Med\\
    How deep are your d\pointup{e}signs!\\
The foolish man cann\pointup{o}t know this\Med\\
    and the fool cannot und\pointup{e}rstand.

Though the wicked spring \pointup{u}p like grass\Med\\
    and all who do ev\pointup{\i}l thrive,\\
they are doomed to be eternall\pointup{y} destroyed.\Med\\
    But you, Lord, are eternally \pointup{o}n high.\\
See how your en\pointup{e}mies perish;\Med\\
    all doers of evil \pointup{a}re scattered.

To me you give the wild \pointup{o}x’s strength;\Med\\
    you anoint me with the pur\pointup{e}st oil.\\
My eyes looked in triumph \pointup{o}n my foes;\Med\\
    my ears heard gladly of th\pointup{e}ir fall.\\
The just will flourish l\pointup{\i}ke the palm-tree\Med\\
    and grow like a Leban\pointup{o}n cedar.

Planted in the house \pointup{o}f the Lord\Med\\
    they will flourish in the courts of \pointup{o}ur God,\\
still bearing fruit when th\pointup{e}y are old,\Med\\
    still full of sap, st\pointup{\i}ll green,\\
to proclaim that the L\pointup{o}rd is just.\Med\\
    In him, my rock, there is n\pointup{o} wrong.

Glory to the Father and t\pointup{o} the Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
    and will be for ever. \pointupl{A}men.
  \end{patverse}
  \end{psalmverse}
