\settowidth{\versewidth}{Their princes were thrown down by the side of the rock; *}
\begin{verse}[\versewidth]
\begin{patverse}
\indentpattern{0101 101 101 101 101 101}
\FirstLetter{I} have called to you, Lord; hast\pointup{e}n to help me!\Med\\
    Hear my voice wh\pointup{e}n I cry to you.\\
Let my prayer arise before y\pointup{o}u like incense,\Med\\
    the raising of my hands like an \pointup{e}vening oblation.

Set, O Lord, a guard \pointup{o}ver my mouth;\Med\\
    keep watch, O Lord, at th\pointup{e} door of my lips!\\
Do not turn my heart to th\pointup{\i}ngs that are wrong,\Med\\
    to evil deeds with m\pointup{e}n who are sinners.

Never allow me to share \pointup{\i}n their feasting.\Med\\
    If a good man strikes or reproves m\pointup{e} it is kindness;\\
but let the oil of the wicked n\pointup{o}t anoint my head.\Med\\
    Let my prayer be ever \pointup{a}gainst their malice.

Their princes were thrown down by the s\pointup{\i}de of the rock;\Med\\
    then they understood th\pointup{a}t my words were kind.\\
As a millstone is shattered to p\pointup{\i}eces on the ground,\Med\\
    so their bones were strewn at th\pointup{e} mouth of the grave.

To you, Lord God, m\pointup{y} eyes are turned:\Med\\
    in you I take r\pointup{e}fuge; spare my soul!\\
From the trap they have laid f\pointup{o}r me keep me safe:\Med\\
    keep me from the snares of th\pointup{o}se who do evil.

Glory to the Father \pointup{a}nd to the Son,\Med\\
    and to th\pointup{e} Holy Spirit:\\
as it was in the beg\pointup{\i}nning, is now,\Med\\
and will be f\pointup{o}r ever. Amen.
\end{patverse}
\end{verse}
