\settowidth{\versewidth}{May the mountains bring forth peace for the people *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 1011 101 101 101 101 101}
\FirstLetter{O} God, give your judgment to th\pointup{e} king,\Med\\
to a king’s son y\pointup{o}ur justice,\\
that he may judge your people \pointup{\i}n justice\Med\\
and your poor in r\pointup{\i}ght judgment.

May the mountains bring forth peace for th\pointup{e} people\Med\\
and the h\pointup{\i}lls, justice.\\
May he defend the poor of the peopl\pointup{e}\Flex\\
and save the children of th\pointup{e} needy\Med\\
and crush the \pointup{o}ppressor.

He shall endure like the sun and th\pointup{e} moon\Med\\
from age t\pointup{o} age.\\
He shall descend like rain on th\pointup{e} meadow,\Med\\
like raindrops on th\pointup{e} earth.

In his days justice sh\pointup{a}ll flourish\Med\\
and peace till the m\pointup{o}on fails.\\
He shall rule from sea t\pointup{o} sea,\Med\\
from the Great River to \pointup{e}arth’s bounds.

Before him his enemies sh\pointup{a}ll fall,\Med\\
his foes lick th\pointup{e} dust.\\
The kings of Tarshish and th\pointup{e} seacoasts\Med\\
shall pay h\pointup{\i}m tribute.

The kings of Sheba \pointup{a}nd Seba\Med\\
shall bring h\pointup{\i}m gifts.\\
Before him all kings shall f\pointup{a}ll prostrate,\Med\\
all nations sh\pointup{a}ll serve him.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
