\settowidth{\versewidth}{Ring out your joy to the Lord, O you just *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01 101 101 101 101 101 101 101 101 101 101 1 101}
    \FirstLetter{R}ing out your joy to the Lord, O y\pointup{o}u just\Med\\
    for praise is fitting for loyal h\pointup{e}arts.

Give thanks to the Lord upon th\pointup{e} lyre\Med\\
    with a ten-stringed harp sing him s\pointup{o}ngs\\
O sing him a song that \pointup{\i}s new\Med\\
    play loudly, with all your sk\pointup{\i}ll.

For the word of the Lord \pointup{\i}s faithful\Med\\
    and all his works to be tr\pointup{u}sted\\
The Lord loves justice \pointup{a}nd right\Med\\
    and fills the earth with his l\pointup{o}ve.

By his word the heavens w\pointup{e}re made\Med\\
    by the breath of his mouth all the st\pointup{a}rs\\
He collects the waves of th\pointup{e} ocean\Med\\
    he stores up the depths of the s\pointup{e}a.

Let all the earth fear the L\pointup{o}rd\Med\\
    all who live in the world rev\pointup{e}re him\\
He spoke; and it came t\pointup{o} be\Med\\
    He commanded; it sprang into b\pointup{e}ing.

He frustrates the designs of th\pointup{e} nations\Med\\
    he defeats the plans of the p\pointup{e}oples\\
His own designs shall stand f\pointup{o}r ever\Med\\
    the plans of his heart from age to \pointup{a}ge.

They are happy, whose God is th\pointup{e} Lord\Med\\
    the people he has chosen as his \pointup{o}wn\\
From the heavens the Lord l\pointup{o}oks forth\Med\\
    he sees all the children of m\pointup{e}n.

From the place where he dwells h\pointup{e} gazes\Med\\
    on all the dwellers on the \pointup{e}arth\\
he who shapes the hearts of th\pointup{e}m all\Med\\
    and considers all their d\pointup{e}eds.

A king is not saved by h\pointup{\i}s army\Med\\
    nor a warrior preserved by his str\pointup{e}ngth\\
A vain hope for safety is th\pointup{e} horse\Med\\
    despite its power it cannot s\pointup{a}ve.

The Lord looks on those who r\pointup{e}vere him\Med\\
    on those who hope in his l\pointup{o}ve\\
to rescue their souls fr\pointup{o}m death\Med\\
    to keep them alive in f\pointup{a}mine.

Our soul is waiting for th\pointup{e} Lord\Med\\
    The Lord is our help and our sh\pointup{\i}eld\\
In him do our hearts f\pointup{\i}nd joy\Med\\
    We trust in his holy n\pointup{a}me.

May your love be upon us, \pointup{O} Lord\Med\\
    as we place all our hope in y\pointup{o}u

Glory to the Father and to th\pointup{e} Son\Med\\
    and to the Holy Sp\pointup{\i}rit\\
as it was in the beginning, \pointup{\i}s now\Med\\
    and will be for ever. Am\pointup{e}n.
  \end{patverse}
\end{psalmverse}
