\begin{verse}
  \begin{patverse}
    \indentpattern{010101 1 010101 1 101 101 101 10101 101 1 101}
\FirstLetter{O} shepherd of Isra\pointup{e}l, hear us,\Med\\
you who lead Jos\pointup{e}ph’s flock,\\
shine forth from your cher\pointup{u}bim throne\Med\\
upon Ephraim, Benjamin, M\pointup{a}nasseh.\\
O Lord, rouse \pointup{u}p your might,\Med\\
O Lord, come to \pointup{o}ur help.

God of hosts br\pointup{\i}ng us back;\Med\\
let your face shine on us and we shall b\pointup{e} saved.

Lord God of h\pointup{o}sts, how long\Med\\
will you frown on your peopl\pointup{e}’s plea?\\
You have fed them with tears f\pointup{o}r their bread,\Med\\
an abundance of tears for th\pointup{e}ir drink.\\
You have made us the taunt \pointup{o}f our neighbors,\Med\\
our enemies laugh us t\pointup{o} scorn.

God of hosts, bring us b\pointup{a}ck;\Med\\
let your face shine on us and we shall b\pointup{e} saved.

You brought a vine \pointup{o}ut of Egypt;\Med\\
to plant it you drove out th\pointup{e} nations.\\
Before it you cl\pointup{e}ared the ground;\Med\\
it took root and spread through th\pointup{e} land.

The mountains were covered w\pointup{\i}th its shadow,\Med\\
the cedars of God with \pointup{\i}ts boughs.\\
It stretched out its branches t\pointup{o} the sea,\Med\\
to the Great River it stretched out \pointup{\i}ts shoots.

Then why have you broken d\pointup{o}wn its walls?\Med\\
It is plucked by all who p\pointup{a}ss by.\\
It is ravaged by the boar \pointup{o}f the forest,\Med\\
devoured by the beasts of th\pointup{e} field.

God of hosts, turn again, w\pointup{e} implore,\Med\\
look down from heaven \pointup{a}nd see.\\
Visit the vine \pointup{a}nd protect it,\Med\\
the vine your right hand h\pointup{a}s planted.\\
Men have burnt it with fire \pointup{a}nd destroyed it.\Med\\
May they perish at the frown of y\pointup{o}ur face.

May your hand be on the man y\pointup{o}u have chosen,\Med\\
the man you have given y\pointup{o}ur strength.\\
And we shall never forsake y\pointup{o}u again;\Med\\
give us life that we may call upon y\pointup{o}ur name.

God of hosts, br\pointup{\i}ng us back;\Med\\
let your face shine on us and we shall b\pointup{e} saved.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{verse}
