\settowidth{\versewidth}{You shall be a glorious crown in the hand of the Lord, *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{010101 101 101 10101 10101 101 101}
\FirstLetter{I} rejoice heartily \pointup{\i}n the Lord,\Med\\
in my God is the joy of m\pointup{y} soul;\\
for he has clothed me with a robe \pointup{o}f salvation,\Med\\
and wrapped me in a mantle \pointup{o}f justice,\\
like a bridegroom adorned w\pointup{\i}th a diadem,\Med\\
like a bride bedecked with h\pointup{e}r jewels.

As the earth brings f\pointup{o}rth its plants,\Med\\
and a garden makes its growth spr\pointup{\i}ng up,\\
so will the Lord God make just\pointup{\i}ce and praise\Med\\
spring up before all th\pointup{e} nations.

For Zion’s sake I will n\pointup{o}t be silent,\Med\\
for Jerusalem’s sake I will not b\pointup{e} quiet,\\
until her vindication shines forth l\pointup{\i}ke the dawn\Med\\
and her victory like a burn\pointup{\i}ng torch.

Nations shall behold your v\pointup{\i}ndication,\Med\\
and all kings y\pointup{o}ur glory;\\
you shall be called by \pointup{a} new name\Med\\
pronounced by the mouth of th\pointup{e} Lord.\\
You shall be a glorious crown in the hand \pointup{o}f the Lord,\Med\\
a royal diadem held by y\pointup{o}ur God.

No more shall men call y\pointup{o}u “Forsaken,”\Med\\
or your land “Des\pointup{o}late,”\\
but you shall be called “M\pointup{y} Delight,”\Med\\
and your land “\pointup{E}spoused.”\\
For the Lord del\pointup{\i}ghts in you,\Med\\
and makes your land h\pointup{\i}s spouse.

As a young man marr\pointup{\i}es a virgin,\Med\\
your Builder shall marr\pointup{y} you;\\
and as a bridegroom rejoices \pointup{\i}n his bride\Med\\
so shall your God rejoice \pointup{\i}n you.

Glory to the Father and t\pointup{o} the Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
    and will be for ever. \pointupl{A}men.
  \end{patverse}
\end{verse}
