\settowidth{\versewidth}{no place to offer first fruits, to find favor with you.}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{011 11 11 1 11 11 11 11 101011 1 101}
\FirstLetter{B}lessed are you, and praisew\pointup{o}rthy,\Flex\\
O Lord, the God of \pointup{o}ur fathers,\Med\\
and glorious forever is y\pointup{o}ur name.

For you are just in all you have d\pointup{o}ne;\Flex\\
all your deeds are faultless, all your w\pointup{a}ys right,\Med\\
and all your judgm\pointup{e}nts proper.

For we have sinned and transgr\pointup{e}ssed\Flex\\
by departing fr\pointup{o}m you,\Med\\
and we have done every kind \pointup{o}f evil.

For your name’s sake, do not deliver us up f\pointup{o}rever,\Med\\
or make void y\pointup{o}ur covenant.

Do not take away your mercy from \pointup{u}s,\Flex\\
for the sake of Abraham, your b\pointup{e}loved,\Med\\
Isaac your servant, and Israel your hol\pointup{y} one,

To whom you promised to multiply their offspr\pointup{\i}ng\Flex\\
like the stars \pointup{o}f heaven,\Med\\
or the sand on the shore of th\pointup{e} sea.

For we are reduced, O Lord, beyond any other nat\pointup{\i}on,\Flex\\
brought low everywhere in the world th\pointup{\i}s day\Med\\
because of \pointup{o}ur sins.

We have in our day no prince, prophet, or lead\pointup{e}r,\Flex\\
no holocaust, sacrifice, oblation, \pointup{o}r incense,\Med\\
no place to offer first fruits, to find favor w\pointup{\i}th you.

But with contrite heart and humbl\pointup{e} spirit\Med\\
let us be r\pointup{e}ceived;\\
as though it were holocausts of rams \pointup{a}nd bullocks,\Med\\
or thousands of f\pointup{a}t lambs,\\
so let our sacrifice be in your presence tod\pointup{a}y\Flex\\
as we follow you unr\pointup{e}servedly;\Med\\
for those who trust in you cannot be put t\pointup{o} shame.

And now we follow you with our wh\pointup{o}le heart,\Med\\
we fear you and we pray t\pointup{o} you.

Glory to the Father and to th\pointup{e} Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
    and will be for ever. \pointupl{A}men.
  \end{patverse}
\end{verse}
