\settowidth{\versewidth}{Behold, the nations count as a drop of the bucket, +}
\begin{verse}[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 1011 1011 11 101 101}
\FirstLetter{H}ere comes with power th\pointup{e} Lord God,\Med\\
who rules by h\pointup{\i}s strong arm;\\
here is his rew\pointup{a}rd with him,\Med\\
his recomp\pointup{e}nse before him.

Like a shepherd he f\pointup{e}eds his flock;\Med\\
in his arms he gath\pointup{e}rs the lambs,\\
Carrying them \pointup{\i}n his bosom,\Med\\
and leading the \pointup{e}wes with care.

Who has cupped in his hand the waters \pointup{o}f the sea,\Med\\
and marked off the heavens w\pointup{\i}th a span?\\
Who has held in a measure the dust of the \pointup{e}arth,\Flex\\
weighed the mount\pointup{a}ins in scales\Med\\
and the hills \pointup{\i}n a balance?

Who has directed the spirit \pointup{o}f the Lord,\Med\\
or has instructed him \pointup{a}s his counselor?\\
Whom did he consult to gain knowl\pointup{e}dge?\Flex\\
Who taught him the p\pointup{a}th of judgment,\Med\\
or showed him the way of \pointup{u}nderstanding?

Behold, the nations count as a drop of the buck\pointup{e}t,\Flex\\
as dust \pointup{o}n the scales;\Med\\
the coastlands weigh no m\pointup{o}re than powder.

Lebanon would not suff\pointup{\i}ce for fuel,\Med\\
nor its animals be enough for h\pointup{o}locausts.\\
Before him all the nations \pointup{a}re as nought,\Med\\
as nothing and void h\pointup{e} accounts them.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the H\pointup{o}ly Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forev\pointup{e}r. Amen.
  \end{patverse}
\end{verse}
