\settowidth{\versewidth}{He knows that wise men and fools must both perish *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 1011 1011 1 101}
\FirstLetter{H}ear this, \pointup{a}ll you peoples,\Med\\
give heed, all who dwell in th\pointup{e} world,\\
men both l\pointup{o}w and high,\Med\\
rich and poor \pointup{a}like!

My lips will speak w\pointup{o}rds of wisdom.\Med\\
My heart is full \pointup{o}f insight.\\
I will turn my mind t\pointup{o} a parable,\Med\\
with the harp I will solve m\pointup{y} problem.

Why should I fear in \pointup{e}vil days\Med\\
the malice of the foes who s\pointup{u}rround me,\\
men who trust \pointup{\i}n their wealth,\Med\\
and boast of the vastness of th\pointup{e}ir riches?

For no man can buy h\pointup{\i}s own ransom,\Med\\
or pay a price to God for h\pointup{\i}s life.\\
The ransom of his soul is beyond h\pointup{\i}m.\Flex\\
He cannot buy life w\pointup{\i}thout end,\Med\\
nor avoid coming to th\pointup{e} grave.

He knows that wise men and fools m\pointup{u}st both perish\Med\\
and leave their wealth t\pointup{o} others.\\
Their graves are their homes for ev\pointup{e}r,\Flex\\
their dwelling place from \pointup{a}ge to age,\Med\\
though their names spread wide through th\pointup{e} land.

In his riches, m\pointup{a}n lacks wisdom:\Med\\
he is like the beasts that are d\pointup{e}stroyed.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
