\settowidth{\versewidth}{“What profit would my death be, my going to the grave? *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{01 101 101 101 101 10101 101}
\FirstLetter{I} will praise you, Lord, you h\pointup{a}ve rescued me\Med\\
and have not let my enemies rejoice ov\pointup{e}r me.

O Lord, I cried to you f\pointup{o}r help\Med\\
and you, my God, h\pointup{a}ve healed me.\\
O Lord, you have raised my soul from th\pointup{e} dead,\Med\\
restored me to life from those who sink into th\pointup{e} grave.

Sing psalms to the Lord, you wh\pointup{o} love him,\Med\\
give thanks to his hol\pointup{y} name.\\
His anger lasts a moment; his favor all thr\pointup{o}ugh life.\Med\\
At night there are tears, but joy comes w\pointup{\i}th dawn.

I said to myself in my g\pointup{o}od fortune:\Med\\
“Nothing will ever d\pointup{\i}sturb me.”\\
Your favor had set me on a mount\pointup{a}in fastness,\Med\\
then you hid your face and I was put to c\pointup{o}nfusion.

To you, Lord, \pointup{I} cried,\Med\\
to my God I made \pointup{a}ppeal:\\
“What profit would my death be, my going to th\pointup{e} grave?\Med\\
Can dust give you praise or proclaim y\pointup{o}ur truth?

The Lord listened and h\pointup{a}d pity.\Med\\
The Lord came to m\pointup{y} help.\\
For me you have changed my mourning int\pointup{o} dancing,\Med\\
you removed my sackcloth and clothed me w\pointup{\i}th joy.\\
So my soul sings psalms to you \pointup{u}nceasingly.\Med\\
O Lord my God, I will thank you f\pointup{o}r ever.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
