\settowidth{\versewidth}{those who boast of their worthless gods. *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 11 11 11 11 101 101}
    \FirstLetter{T}he Lord is king, let \pointup{e}arth rejoice,\Med\\
let all the coastlands b\pointup{e} glad.\\
Cloud and darkness \pointup{a}re his raiment;\Med\\
his throne, justice \pointup{a}nd right.

A fire prep\pointup{a}res his path;\Med\\
it burns up his foes on ever\pointup{y} side.\\
His lightnings light \pointup{u}p the world,\Med\\
the earth trembles at th\pointup{e} sight.

The mountains m\pointup{e}lt like wax\Med\\
before the Lord of all th\pointup{e} earth.\\
The skies procl\pointup{a}im his justice;\Med\\
all peoples see h\pointup{\i}s glory.

Let those who serve idols be ash\pointup{a}med,\Flex\\
those who boast of their w\pointup{o}rthless gods.\Med\\
All you spirits, worsh\pointup{\i}p him.

Zion hears and is gl\pointup{a}d;\Flex\\
the people of Jud\pointup{a}h rejoice\Med\\
because of your judgments, \pointup{O} Lord.

For you indeed are the L\pointup{o}rd\Flex\\
most high ab\pointup{o}ve all the earth,\Med\\
exalted far above \pointup{a}ll spirits.

The Lord loves those who hate ev\pointup{\i}l;\Flex\\
he guards the souls \pointup{o}f his saints;\Med\\
he sets them free from th\pointup{e} wicked.

Light shines forth f\pointup{o}r the just\Med\\
and joy for the upright \pointup{o}f heart.\\
Rejoice, you just, \pointup{\i}n the Lord;\Med\\
give glory to his hol\pointup{y} name.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men.
  \end{patverse}
\end{psalmverse}
