\hymn

\settowidth{\versewidth}{Mary, crowned with living light,}

\begin{hymnverse}%%[\versewidth]
Mary, crowned with living light,\\
Temple of the Lord,\\
Place of peace and holiness,\\
Shelter of the Word.

Mystery of sinless life\\
In our fallen race,\\
Free from shadow, you reflect\\
Plentitude of grace.

Virgin Mother of our God,\\
Lift us when we fall,\\
Who were named upon the Cross\\
Mother of us all.

Father, Son and Holy Ghost,\\
Heaven sings your praise;\\
Mary magnifies your name\\
Through eternal days.
\end{hymnverse}

\begin{hymnsource}
Tune: Tune: Glorification 75.75

Music: \emph{Gossner’s Choralbuch}, Leipzig, 1832

Text: © Stanbrook Abbey, used with permission



<a href=#psalm>Go to the Psalmody</a>



<span class=rubrica>Or:



Word Eternal of the Father,

Uttered long before all time, 

He is Alpha and Omega,

All creation’s Source and End;

Past and present and the future

Flow from his most Holy Will.

Jesus, Lord, Emmanuel!



He assumed our human nature, 

Doomed to death by Adam’s fall;

God and Man, he came to save us, 

Loving all that he had made, 

From the law that would condemn us

To the pains of endless woe. 

Jesus, Lord, Emmanuel!



Blest indeed that birth so holy, 

When the spotless Virgin pure,

Rendered fruitful by the Spirit,

Brought our great Redeemer forth,

And at last the Infant Savior

Smiled upon his treasured world

Jesus, Lord, Emmanuel!



He whom ancient seers promised

In their songs of long ago

Whom the prophets’ faithful pages

Oft foretold as soon to come,

Now at last he is among us,

Let us all his praises sing:

Jesus, Lord, Emmanuel!



Let us sing to God the Father,

In sweet tones of melody,

And to God the Holy Spirit

Never ending glory be,

As we praise with grateful voices

Him whom Virgin Mother bore:

Jesus, Lord, Emmanuel!



<span class=citazione>Tune: Divinum Mysterium 87.87.877

Music: \emph{Piae Cantiones}, 1582

Text: \emph{Corde natus}

Translation: © the Benedictines of Saint Cecilia’s Abbey, Ryde, UK, used with permission.

\end{hymnsource}