\settowidth{\versewidth}{Let them praise the name of the Lord. *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 101 101 101 101}
\FirstLetter{P}raise the Lord fr\pointup{o}m the heavens,\Med\\
    praise him in th\pointup{e} heights.\\
Praise him, \pointup{a}ll his angels,\Med\\
    praise him, all h\pointup{\i}s host.

Praise him, s\pointup{u}n and moon,\Med\\
    praise him, shin\pointup{\i}ng stars.\\
Praise him, h\pointup{\i}ghest heavens\Med\\
    and the waters above th\pointup{e} heavens.

Let them praise the name \pointup{o}f the Lord.\Med\\
    He commanded: they w\pointup{e}re made.\\
He fixed th\pointup{e}m for ever,\Med\\
    gave a law which shall not pass \pointup{a}way.

Praise the Lord fr\pointup{o}m the earth,\Med\\
    sea creatures and \pointup{a}ll oceans,\\
fire and hail, sn\pointup{o}w and mist,\Med\\
    stormy winds that obey h\pointup{\i}s word;

all mount\pointup{a}ins and hills,\Med\\
    all fruit trees \pointup{a}nd cedars,\\
beasts, w\pointup{\i}ld and tame,\Med\\
    reptiles and birds on th\pointup{e} wing;

all earth’s k\pointup{\i}ngs and peoples,\Med\\
    earth’s princes \pointup{a}nd rulers,\\
young m\pointup{e}n and maidens,\Med\\
    old men together w\pointup{\i}th children.

Let them praise the name \pointup{o}f the Lord\Med\\
    for he alone is \pointup{e}xalted.\\
The splendour \pointup{o}f his name\Med\\
    reaches beyond heaven \pointup{a}nd earth.

He exalts the strength \pointup{o}f his people.\Med\\
    He is the praise of all h\pointup{\i}s saints,\\
of the s\pointup{o}ns of Israel,\Med\\
    of the people to whom he c\pointup{o}mes close.

Glory to the Father and t\pointup{o} the Son,\Med\\
    and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
    and will be for ever. \pointupl{A}men.
  \end{patverse}
\end{verse}
