\begin{psalmverse}
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 101 101 101 101 101}
    \FirstLetter{T}he Lord is great and worthy to b\pointup{e} praised\Med\\
in the city of \pointup{o}ur God.\\
His holy mountain rises \pointup{\i}n beauty,\Med\\
the joy of all th\pointup{e} earth.

Mount Zion, true pole of th\pointup{e} earth,\Med\\
the Great K\pointup{\i}ng’s city!\\
God, in the midst of \pointup{\i}ts citadels,\Med\\
has shown himself \pointup{\i}ts stronghold.

For the kings assembled t\pointup{o}gether,\Med\\
together they \pointup{a}dvanced.\\
They saw; at once they were \pointup{a}stounded;\Med\\
dismayed, they fled \pointup{\i}n fear.

A trembling seized th\pointup{e}m there,\Med\\
like the pangs \pointup{o}f birth.\\
By the east wind you have d\pointup{e}stroyed\Med\\
the ships \pointup{o}f Tarshish.

As we have heard, so we h\pointup{a}ve seen\Med\\
in the city of \pointup{o}ur God,\\
in the city of the Lord \pointup{o}f hosts\Med\\
which God upholds f\pointup{o}r ever.

O God, we ponder y\pointup{o}ur love\Med\\
within y\pointup{o}ur temple.\\
Your praise, O God, like y\pointup{o}ur name\Med\\
reaches the ends of th\pointup{e} earth.

With justice your right hand \pointup{\i}s filled.\Med\\
Mount Zion r\pointup{e}joices;\\
the people of Judah r\pointup{e}joice\Med\\
at the sight of y\pointup{o}ur judgments.

Walk through Zion, walk \pointup{a}ll round it;\Med\\
count the number of \pointup{\i}ts towers.\\
Review all \pointup{\i}ts ramparts,\Med\\
examine \pointup{\i}ts castles,

that you may tell the next gen\pointup{e}ration\Med\\
that such is \pointup{o}ur God,\\
our God for ever \pointup{a}nd always.\Med\\
It is he wh\pointup{o} leads us.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
