\settowidth{\versewidth}{A scepter of justice is the scepter of your kingdom. *}
\begin{psalmverse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{011 11 11 11 11 11 11 101}
\FirstLetter{M}y heart overflows with noble w\pointup{o}rds.\Flex\\
To the king I must speak the song I h\pointup{a}ve made,\Med\\
my tongue as nimble as the pen of \pointup{a} scribe.

You are the fairest of the children of m\pointup{e}n\Flex\\
and graciousness is poured upon y\pointup{o}ur lips:\Med\\
because God has blessed you for ev\pointup{e}rmore.

O mighty one, gird your sword upon your th\pointup{\i}gh;\Flex\\
in splendor and state, ride on \pointup{\i}n triumph\Med\\
for the cause of truth and goodness \pointup{a}nd right.

Take aim with your bow in your dread right h\pointup{a}nd.\Flex\\
Your arrows are sharp, peoples fall b\pointup{e}neath you.\Med\\
The foes of the king fall down and l\pointup{o}se heart.

Your throne, O God, shall endure for \pointup{e}ver.\Flex\\
A scepter of justice is the scepter of y\pointup{o}ur kingdom.\Med\\
Your love is for justice; your hatred f\pointup{o}r evil.

Therefore God, your God, has anointed y\pointup{o}u\Flex\\
with the oil of gladness above oth\pointup{e}r kings:\Med\\
your robes are fragrant with aloes \pointup{a}nd myrrh.

From the ivory palace you are greeted with mus\pointup{\i}c.\Flex\\
The daughters of kings are among y\pointup{o}ur loved ones.\Med\\
On your right stands the queen in gold \pointup{o}f Ophir.

Glory to the Father and to th\pointup{e} Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginning, \pointup{\i}s now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{psalmverse}
