\settowidth{\versewidth}{To the gates of the nether world I shall be consigned *}
\begin{verse}%%[\versewidth]
  \begin{patverse}
    \indentpattern{0101 101 101 101 101 101 101 101 101 101}
    \FirstLetter{O}nce \pointup{I} said,\Med\\
“In the noontime of life I must d\pointup{e}part!\\
To the gates of the nether world I shall b\pointup{e} consigned\Med\\
for the rest of m\pointup{y} years.”

I said, “I shall see the L\pointup{o}rd no more\Med\\
in the land of th\pointup{e} living.\\
No longer shall I behold my f\pointup{e}llow men\Med\\
among those who dwell in th\pointup{e} world.”

My dwelling, like a sh\pointup{e}pherd’s tent,\Med\\
is struck down and borne away fr\pointup{o}m me;\\
you have folded up my life, l\pointup{\i}ke a weaver\Med\\
who severs the l\pointup{a}st thread.

Day and night you give me ov\pointup{e}r to torment;\Med\\
I cry out until th\pointup{e} dawn.\\
Like a lion he breaks \pointup{a}ll my bones;\Med\\
day and night you give me over t\pointup{o} torment.

Like a swallow I utt\pointup{e}r shrill cries;\Med\\
I moan like \pointup{a} dove.\\
My eyes grow weak, g\pointup{a}zing heaven-ward:\Med\\
O Lord, I am in straits; be m\pointup{y} surety!

You have pres\pointup{e}rved my life\Med\\
from the pit of d\pointup{e}struction,\\
when you cast beh\pointup{\i}nd your back\Med\\
all m\pointup{y} sins.

For it is not the nether world that g\pointup{\i}ves you thanks,\Med\\
nor death that prais\pointup{e}s you;\\
Neither do those who go down int\pointup{o} the pit\Med\\
await y\pointup{o}ur kindness.

The living, the living g\pointup{\i}ve you thanks,\Med\\
as I do t\pointup{o}day.\\
Fathers declare t\pointup{o} their sons,\Med\\
O God, your faithf\pointup{u}lness.

The Lord \pointup{\i}s our savior;\Med\\
we shall sing to stringed instr\pointup{u}ments\\
in the house \pointup{o}f the Lord\Med\\
all the days of \pointup{o}ur life.

Glory to the Father and t\pointup{o} the Son,\Med\\
and to the Hol\pointup{y} Spirit:\\
as it was in the beginn\pointup{\i}ng, is now,\Med\\
and will be forever. \pointupl{A}men. 
  \end{patverse}
\end{verse}
